---
title: "Results"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
fontsize: 10
fontfamily: arev
header-includes:
- \usepackage{caption}
- "\\captionsetup[table]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
  - \\usepackage{setspace}\\doublespacing - \\usepackage{float}"
---

```{r setup, include=FALSE, echo=FALSE, warning=FALSE}
```

```{r setup, include=FALSE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(tidyverse)
library(lmerTest)
library(lme4)
library(car)
library(buildmer)
library(interactions)
library(glmnet)
library(lubridate)
library(dplyr, warn.conflicts = FALSE)
library(broom)
library(ggplot2)
library(tinytex)
# install.packages('plyr', repos="http://cran.us.r-project.org")

# Function to create the date numbering
create_date_numbering <- function(df, column, start, direction = "backward") {
  df %>%
    mutate(
      # Use !!sym() to handle column names passed as strings
      Date = as_date(!!sym(column), format = "%B %d, %Y %I:%M %p"),
      
      # Conditional logic for date indexing
      Date_Index = if(direction == "backward") {
        -as.numeric(difftime(as.Date(start), Date, units = "days"))
      } else {
        as.numeric(difftime(Date, as.Date(start), units = "days"))
      }
    )
}

# Read and process pre-data
data_pre <- read.csv("Before_Stereotypes_Proportion_LIWC_Hate.csv") %>%
  mutate(Condition_Contrast = -0.5) %>%
  create_date_numbering("Before_Dates", "2023-10-06", direction = "backward") %>% filter(Date_Index >= -365) # Ensure min index is at least -365

# Read and process post-data
data_post <- read.csv("After_Stereotypes_Proportion_LIWC_Hate.csv") %>%
  mutate(Condition_Contrast = 0.5) %>%
  create_date_numbering("After_Dates", "2023-10-07", direction = "forward")

# Optional: Verify the results
head(data_pre[, c("Before_Dates", "Date", "Date_Index")])
head(data_post[, c("After_Dates", "Date", "Date_Index")])


data = merge(data_pre, data_post, 
             by=names(data_pre)[names(data_pre) %in% names(data_post)],
             all = TRUE) %>% 
  distinct()

data = data %>%
  mutate(ethnorace_israelijewish = prop_Israeli + prop_Jewish,
         ethnorace_arabicmuslim = prop_Arabic + prop_Muslim) %>%
  mutate(Ethnorace = ifelse(ethnorace_israelijewish > ethnorace_arabicmuslim, -0.5,
                            ifelse(ethnorace_arabicmuslim > ethnorace_israelijewish, 0.5, NA))) %>%
  mutate(Militant = ifelse(Condition_Contrast == 0.5 & prop_IDF > prop_Hamas, -0.5,
                           ifelse(Condition_Contrast == 0.5 & prop_Hamas > prop_IDF, 0.5,  NA))) %>%
  mutate(Civilian = ifelse(prop_IDF > ethnorace_israelijewish, -0.5,
                           ifelse(prop_Hamas > ethnorace_arabicmuslim, -0.5,
                                  ifelse(ethnorace_israelijewish > prop_IDF, 0.5,
                                         ifelse(ethnorace_arabicmuslim > prop_Hamas, 0.5, NA))))) %>%
  mutate(
    Ethnorace = factor(Ethnorace,
                       levels = c(-0.5, 0.5),
                       labels = c("Israeli and/or Jewish group", "Arabic and/or Muslim group")),
    Militant = factor(Militant,
                       levels = c(-0.5, 0.5),
                       labels = c("IDF", "Hamas")),
    Affiliation_Contrast = factor(Affiliation_Contrast,
                                  levels = c(-0.5, 0.5),
                                  labels = c("Right-leaning", "Left-leaning")),
    Condition_Contrast = factor(Condition_Contrast,
                                levels = c(-0.5, 0.5),
                                labels = c("Before 10/07/23", "After 10/07/23")),
  )
```

```{r setup, include=FALSE, echo=FALSE, warning=FALSE}
```

# Change in Negative Sentiment

Intercept as indicated by the Pre-reg

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in negative sentiment in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_negsentiment = lmer(tone_neg ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1+Ethnorace*Condition_Contrast|Subject_ID), data=data)

#| echo: false
kable(summary(mod_negsentiment)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot1, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- cat_plot(mod_negsentiment,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                    colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Negative Sentiment",
        color = "Political Affiliation"
      ) 

 # Print the plot
 print(p)
```
Changes in negative sentiment in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_negsentiment = lmer(tone_neg ~ Ethnorace*Affiliation_Contrast*Date_Index + (1+Ethnorace*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_negsentiment)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot2, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_negsentiment,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      labs(
        x = "Dates Before and After Oct 7th, 2023",
        y = "Negative Sentiment",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
### Tweets Mentioning either IDF or Hamas

Changes in negative sentiment in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_negsentiment = lmer(tone_neg ~ Militant*Affiliation_Contrast*Date_Index + (1+Militant*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_negsentiment)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot3, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_negsentiment,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Dates After Oct 7th, 2023",
        y = "Negative Sentiment",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 

 # Print the plot
 print(p)
```
Simplified Intercept

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in negative sentiment in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_negsentiment = lmer(tone_neg ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1|Subject_ID), data=data)

#| echo: false
kable(summary(mod_negsentiment)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot4, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- cat_plot(mod_negsentiment,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Negative Sentiment",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 
   # # Add vertical line at 0 with date label
   # geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   # annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
   #          vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
Changes in negative sentiment in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_negsentiment = lmer(tone_neg ~ Ethnorace*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_negsentiment)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```

```{r interaction-plot5, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_negsentiment,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date Before and After Oct 7th, 2023",
        y = "Negative Sentiment",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

### Tweets Mentioning either IDF or Hamas

Changes in negative sentiment in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_negsentiment = lmer(tone_neg ~ Militant*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_negsentiment)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```

```{r interaction-plot6, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_negsentiment,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Dates After Oct 7th, 2023",
        y = "Negative Sentiment",
        # color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 
# +
#    # Add vertical line at 0 with date label
#    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
#    annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
#             vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
Significant 2-way interaction
```{r, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_negsentiment,
                    pred = Date_Index,
                    modx = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("blue", "darkgreen")) +
      # Customize labels if needed
      labs(
        x = "Dates After Oct 7th, 2023",
        y = "Negative Sentiment",
        # color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 
# +
#    # Add vertical line at 0 with date label
#    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
#    annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
#             vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
# Change in Positive Sentiment

Intercept as indicated by the Pre-reg

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in positive sentiment in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_possentiment = lmer(tone_pos ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1+Ethnorace*Condition_Contrast|Subject_ID), data=data)


#| echo: false
kable(summary(mod_possentiment)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot7, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- cat_plot(mod_possentiment,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Positive Sentiment",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 
   # # Add vertical line at 0 with date label
   # geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   # annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
   #          vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
Changes in positive sentiment in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_possentiment = lmer(tone_pos ~ Ethnorace*Affiliation_Contrast*Date_Index + (1+Ethnorace*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_possentiment)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot8, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_possentiment,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date Before and After Oct 7th, 2023",
        y = "Positive Sentiment",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
### Tweets Mentioning either IDF or Hamas

Changes in positve sentiment in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_possentiment = lmer(tone_pos ~ Militant*Affiliation_Contrast*Date_Index + (1+Militant*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_possentiment)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot9, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_possentiment,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date After Oct 7th, 2023",
        y = "Positive Sentiment",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
Simplified Intercept

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in positive sentiment in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_possentiment = lmer(tone_pos ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1|Subject_ID), data=data)

#| echo: false
kable(summary(mod_possentiment)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot10, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- cat_plot(mod_possentiment,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Positive Sentiment",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 
   # # Add vertical line at 0 with date label
   # geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   # annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
   #          vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
Changes in positive sentiment in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_possentiment = lmer(tone_pos ~ Ethnorace*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_possentiment)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot11, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_possentiment,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Dates Before and After Oct 7th, 2023",
        y = "Positive Sentiment",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```


# Change in Warm-conveying Words

Intercept as indicated by the Pre-reg

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in Warm-conveying Words in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_warmstereotype = lmer(prop_Warm ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1+Ethnorace*Condition_Contrast|Subject_ID), data=data)


#| echo: false
kable(summary(mod_warmstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot12, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- cat_plot(mod_warmstereotype,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Warm-conveying Words",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 
   # # Add vertical line at 0 with date label
   # geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   # annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
   #          vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
Changes in Warm-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_warmstereotype = lmer(prop_Warm ~ Ethnorace*Affiliation_Contrast*Date_Index + (1+Ethnorace*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_warmstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot13, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_warmstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date Before and After Oct 7th, 2023",
        y = "Warm-conveying Words",
        # color = "Condition",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
### Tweets Mentioning either IDF or Hamas

Changes in Warm-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_warmstereotype = lmer(prop_Warm ~ Militant*Affiliation_Contrast*Date_Index + (1+Militant*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_warmstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot14, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_warmstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date After Oct 7th, 2023",
        y = "Warm-conveying Words",
        # color = "Condition",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
Simplified Intercept

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in Warm-conveying Words in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_warmstereotype = lmer(prop_Warm ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1|Subject_ID), data=data)

#| echo: false
kable(summary(mod_warmstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot15, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- cat_plot(mod_warmstereotype,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Warm-conveying Words",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 
   # # Add vertical line at 0 with date label
   # geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   # annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
   #          vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
Changes in Warm-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_warmstereotype = lmer(prop_Warm ~ Ethnorace*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_warmstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```

```{r interaction-plot16, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_warmstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date Before and After Oct 7th, 2023",
        y = "Warm-conveying Words",
        # color = "Condition",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
### Tweets Mentioning either IDF or Hamas

Changes in Warm-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_warmstereotype = lmer(prop_Warm ~ Militant*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_warmstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot17, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_warmstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date After Oct 7th, 2023",
        y = "Warm-conveying Words",
        # color = "Condition",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

# Change in Cold-conveying Words

Intercept as indicated by the Pre-reg

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in Cold-conveying Words in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_coldstereotype = lmer(prop_Cold ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1+Ethnorace*Condition_Contrast|Subject_ID), data=data)


#| echo: false
kable(summary(mod_coldstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot18, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- cat_plot(mod_coldstereotype,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Cold-conveying Words",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 
   # # Add vertical line at 0 with date label
   # geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   # annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
   #          vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
Changes in Cold-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_coldstereotype = lmer(prop_Cold ~ Ethnorace*Affiliation_Contrast*Date_Index + (1+Ethnorace*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_coldstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot19, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_coldstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date After Oct 7th, 2023",
        y = "Cold-conveying Words",
        # color = "Condition",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
### Tweets Mentioning either IDF or Hamas

Changes in Cold-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_coldstereotype = lmer(prop_Cold ~ Militant*Affiliation_Contrast*Date_Index + (1+Militant*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_coldstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot20, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_coldstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date After Oct 7th, 2023",
        y = "Cold-conveying Words",
        # color = "Condition",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

Simplified Intercept

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in Cold-conveying Words in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_coldstereotype = lmer(prop_Cold ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1|Subject_ID), data=data)

#| echo: false
kable(summary(mod_coldstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot21, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- cat_plot(mod_coldstereotype,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Cold-conveying Words",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 
   # # Add vertical line at 0 with date label
   # geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   # annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
   #          vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

Changes in Cold-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_coldstereotype = lmer(prop_Cold ~ Ethnorace*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_coldstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot22, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_coldstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Dates Before and After Oct 7th, 2023",
        y = "Cold-conveying Words",
        # color = "Condition",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

### Tweets Mentioning either IDF or Hamas

Changes in Cold-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_coldstereotype = lmer(prop_Cold ~ Militant*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_coldstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot24, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_coldstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date Before and After Oct 7th, 2023",
        y = "Cold-conveying Words",
        # color = "Condition",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```




# Change in Competence-conveying Words

Intercept as indicated by the Pre-reg

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in Competence-conveying Words in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_compstereotype = lmer(prop_Competence ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1+Ethnorace*Condition_Contrast|Subject_ID), data=data)


#| echo: false
kable(summary(mod_compstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- cat_plot(mod_compstereotype,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                    colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Competence-conveying Words",
        color = "Political Affiliation",
      ) 
 print(p)
```


Changes in Competence-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_compstereotype = lmer(prop_Competence ~ Ethnorace*Affiliation_Contrast*Date_Index + (1+Ethnorace*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_compstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_compstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date After Oct 7th, 2023",
        y = "Competence-conveying Words",
        # color = "Condition",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
### Tweets Mentioning either IDF or Hamas

Changes in Competence-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_compstereotype = lmer(prop_Competence ~ Militant*Affiliation_Contrast*Date_Index + (1+Militant*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_compstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot200, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_compstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date After Oct 7th, 2023",
        y = "Competence-conveying Words",
        # color = "Condition",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

Simplified Intercept

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in Competence-conveying Words in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_compstereotype = lmer(prop_Competence ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1|Subject_ID), data=data)

#| echo: false
kable(summary(mod_compstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot210, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- cat_plot(mod_compstereotype,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Competence-conveying Words",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 

 # Print the plot
 print(p)
```
```{r, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- cat_plot(mod_compstereotype,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                    colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Competence-conveying Words",
        color = "Political Affiliation",
      ) 
 print(p)
```
Changes in Competence-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_compstereotype = lmer(prop_Competence ~ Ethnorace*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_compstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot220, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_compstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Dates Before and After Oct 7th, 2023",
        y = "Competence-conveying Words",
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
```{r, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_compstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Dates Before and After Oct 7th, 2023",
        y = "Competence-conveying Words",
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

### Tweets Mentioning either IDF or Hamas

Changes in Competence-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_compstereotype = lmer(prop_Competence ~ Militant*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_compstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot240, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_compstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date Before and After Oct 7th, 2023",
        y = "Competence-conveying Words",
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
```{r interaction-plot240, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_compstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date Before and After Oct 7th, 2023",
        y = "Competence-conveying Words",
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

# Change in Incompetence-conveying Words

Intercept as indicated by the Pre-reg

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in Incompetence-conveying Words in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_incompstereotype = lmer(prop_Incompetence ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1+Ethnorace*Condition_Contrast|Subject_ID), data=data)


#| echo: false
kable(summary(mod_incompstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot230, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- cat_plot(mod_incompstereotype,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                    colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Incompetence-conveying Words",
        color = "Political Affiliation",
      ) 
 print(p)
```

Changes in Incompetence-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_incompstereotype = lmer(prop_Incompetence ~ Ethnorace*Affiliation_Contrast*Date_Index + (1+Ethnorace*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_incompstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot241, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_incompstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date After Oct 7th, 2023",
        y = "Incompetence-conveying Words"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
### Tweets Mentioning either IDF or Hamas

Changes in Incompetence-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_incompstereotype = lmer(prop_Incompetence ~ Militant*Affiliation_Contrast*Date_Index + (1+Militant*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_incompstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot25, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_incompstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date After Oct 7th, 2023",
        y = "Incompetence-conveying Words",
        # color = "Condition",
        # linetype = "Affiliation"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

Simplified Intercept

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in Incompetence-conveying Words in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_incompstereotype = lmer(prop_Incompetence ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1|Subject_ID), data=data)

#| echo: false
kable(summary(mod_incompstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot26, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- cat_plot(mod_incompstereotype,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Incompetence-conveying Words",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 

 # Print the plot
 print(p)
```
```{r, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- cat_plot(mod_incompstereotype,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Incompetence-conveying Words",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 

 # Print the plot
 print(p)
```


Changes in Incompetence-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_incompstereotype = lmer(prop_Incompetence ~ Ethnorace*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_incompstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r interaction-plot27, fig.width=10, fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_incompstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Dates Before and After Oct 7th, 2023",
        y = "Incompetence-conveying Words",
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```
```{r , fig.height=7,  echo=FALSE, warning=FALSE}

p <- interact_plot(mod_incompstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Dates Before and After Oct 7th, 2023",
        y = "Incompetence-conveying Words",
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```



### Tweets Mentioning either IDF or Hamas

Changes in Incompetence-conveying Words in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_incompstereotype = lmer(prop_Incompetence ~ Militant*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_incompstereotype)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_incompstereotype,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date Before and After Oct 7th, 2023",
        y = "Incompetence-conveying Words",
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```



# Change in Hate-speech Content

Intercept as indicated by the Pre-reg

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in Incompetence-conveying Words in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_hatespeech = lmer(Hate_Score ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1+Ethnorace*Condition_Contrast|Subject_ID), data=data)


#| echo: false
kable(summary(mod_hatespeech)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- cat_plot(mod_hatespeech,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                    colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Hate Speech Content",
        color = "Political Affiliation",
      ) 
 print(p)
```

Changes in Hate Speech Content in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_hatespeech = lmer(Hate_Score ~ Ethnorace*Affiliation_Contrast*Date_Index + (1+Ethnorace*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_hatespeech)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_hatespeech,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date After Oct 7th, 2023",
        y = "Hate Speech Content"
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

### Tweets Mentioning either IDF or Hamas

Changes in Hate Speech Content in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_hatespeech = lmer(Hate_Score ~ Militant*Affiliation_Contrast*Date_Index + (1+Militant*Date_Index|Subject_ID), data=data)

#| echo: false
kable(summary(mod_hatespeech)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_hatespeech,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Date After Oct 7th, 2023",
        y = "Hate Speech Content",
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

Simplified Intercept

### Tweets Mentioning either Israeli and/or Jewish people or Arabic and/or Muslim people

Changes in Hate Speech Content in tweets by the "Before" and "After" period

```{r, echo=FALSE, warning=FALSE}
mod_hatespeech = lmer(Hate_Score ~ Ethnorace*Affiliation_Contrast*Condition_Contrast + (1|Subject_ID), data=data)

#| echo: false
kable(summary(mod_hatespeech)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r, fig.width=10, fig.height=7,echo=FALSE, warning=FALSE}

p <- cat_plot(mod_hatespeech,
                    pred = Condition_Contrast,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.1,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Period Before and After Oct 7th, 2023",
        y = "Hate Speech Content",
        color = "Political Affiliation",
        # linetype = "Affiliation"
      ) 

 # Print the plot
 print(p)
```

Changes in Hate Speech Content in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362)

```{r, echo=FALSE, warning=FALSE}
mod_hatespeech = lmer(Hate_Score ~ Ethnorace*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_hatespeech)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r, fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_hatespeech,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Ethnorace,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Dates Before and After Oct 7th, 2023",
        y = "Hate Speech Content",
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```

### Tweets Mentioning either IDF or Hamas

Changes in Hate Speech Content in tweets between as date index (e.g., 10/07/23 as 0) moving backwards (min= -360) and forward (max= 362). \n Note: IDF was not mentioned in any tweets between 10/07/22 and 10/06/23 (the "Before" period). So, the data was subsetted to only the ""After" period.

```{r, echo=FALSE, warning=FALSE}
mod_hatespeech = lmer(Hate_Score ~ Militant*Affiliation_Contrast*Date_Index + (1|Subject_ID), data=data)
#| echo: false
kable(summary(mod_hatespeech)$coef, 
      caption = "Model Summary", 
      format = "pipe")
```
```{r , fig.width=10, fig.height=7, echo=FALSE, warning=FALSE}

p <- interact_plot(mod_hatespeech,
                    pred = Date_Index,
                    modx = Affiliation_Contrast,
                    mod2 = Militant,
                    plot.points = TRUE,
                    point.alpha = 0.2,
                    interval = TRUE,
                     colors = c("red", "blue")) +
      # Customize labels if needed
      labs(
        x = "Dates Before and After Oct 7th, 2023",
        y = "Hate Speech Content",
      ) +
   # Add vertical line at 0 with date label
   geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
   annotate("text", x = 0, y = Inf, label = "Oct 7th, 2023",
            vjust = 1.5, hjust = 0.5, color = "gray50")

 # Print the plot
 print(p)
```