---
title: "Results"
output: word_document
fontsize: 12
fontfamily: arev
header-includes:
   - \usepackage{caption}
   - \captionsetup[table]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
    - \usepackage{setspace}\doublespacing
    - \usepackage{float}
---
```{r setup, include=FALSE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
# s1_mod1 = lmer(MoneyTrusted ~ agency_contrast*generosity_contrast1*status_contrast*Round +
#               (1|Subject), data = data)
# s1_mod2 = lmer(MoneyTrusted ~ agency_contrast*generosity_contrast1*status_contrast*Feedback + Game_Number +
#               (1|Subject), data=data_firstroundexcluded)
# s2_mod1 = lmer(MoneyTrusted ~ agency_contrast*generosity_contrast1*status_contrast*Round +
#               (1|Subject), data = data)
# s2_mod2 = lmer(MoneyTrusted ~ agency_contrast*generosity_contrast1*status_contrast*Feedback + Game_Number +
#               (1|Subject), data=data_firstroundexcluded)

s1_mod1_statstable = read.csv("s1_mod1_statstable.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)
s1_mod2_statstable = read.csv("s1_mod2_statstable.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)
s2_mod1_statstable = read.csv("s2_mod1_statstable.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)
s2_mod2_statstable = read.csv("s2_mod2_statstable.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)

s1_mod1_sigslopes1 = read.csv("s1_mod1_sigslopes1.csv", stringsAsFactors = FALSE, 
                              na.strings = c("", "NA"), check.names = FALSE)
s1_mod1_sigslopes2 = read.csv("s1_mod1_sigslopes2.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)
s1_mod1_sigslopes3 = read.csv("s1_mod1_sigslopes3.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)

s1_mod2_sigslopes1 = read.csv("s1_mod2_sigslopes1.csv", stringsAsFactors = FALSE, 
                              na.strings = c("", "NA"), check.names = FALSE)
s1_mod2_sigslopes2 = read.csv("s1_mod2_sigslopes2.csv", stringsAsFactors = FALSE, 
                              na.strings = c("", "NA"), check.names = FALSE)
s1_mod2_sigslopes3 = read.csv("s1_mod2_sigslopes3.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)

s2_mod1_sigslopes1 = read.csv("s2_mod1_sigslopes1.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)

s2_mod2_sigslopes1 = read.csv("s2_mod2_sigslopes1.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)
s2_mod2_sigslopes2 = read.csv("s2_mod2_sigslopes2.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)
s2_mod2_sigslopes3 = read.csv("s2_mod2_sigslopes3.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)
s2_mod2_sigslopes4 = read.csv("s2_mod2_sigslopes4.csv", stringsAsFactors = FALSE,
                              na.strings = c("", "NA"), check.names = FALSE)
```

We hypothesized that agency, status, and reciprocity would interact over time to affect trust. We tested the interaction of agency, status, reciprocity, and round as a predictor of trust. We also tested a second model, testing the interaction of agency, status, reciprocity, and feedback as a predictor of trust.  

We therefore tested two models. In the first model we entered entered agency, status, generosity, and round number as interacting predictors of trust. We included the first rounds in this analysis. In the second model we entered agency, status, generosity, and feedback as interacting predictors of trust, with game number as a covariate. For this model, we used removed the first round of each game as no feedback has been received that could affect behavior in the first round. 

# Study 1

Study 1 was a mixed design, with one between-subjects factor (agency: human, AI) and three within-subjects factors (status: high, low; generosity: greedy, neutral, generous; feedback: 9 rounds). 

## Model 1

```{r, include=FALSE, echo=FALSE, warning=FALSE}
s1_mod1_beta_generosity = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate"), "B"]
s1_mod1_se_generosity = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate"), "SE"]
s1_mod1_t_generosity = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate"), "t-value"]
s1_mod1_p_generosity = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate"), "p-value"]
s1_mod1_CI_generosity = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate"), "95% CI"]

s1_mod1_beta_status = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Status"), "B"]
s1_mod1_se_status = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Status"), "SE"]
s1_mod1_t_status = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Status"), "t-value"]
s1_mod1_p_status = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Status"), "p-value"]
s1_mod1_CI_status = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Status"), "95% CI"]

s1_mod1_beta_round = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Round"), "B"]
s1_mod1_se_round = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Round"), "SE"]
s1_mod1_t_round = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Round"), "t-value"]
s1_mod1_p_round = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Round"), "p-value"]
s1_mod1_CI_round = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Round"), "95% CI"]

s1_mod1_beta_generosityround = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate x Round"), "B"]
s1_mod1_se_generosityround = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate x Round"), "SE"]
s1_mod1_t_generosityround = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate x Round"), "t-value"]
s1_mod1_p_generosityround = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate x Round"), "p-value"]
s1_mod1_CI_generosityround = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate x Round"), "95% CI"]

s1_mod1_beta_statusround = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Status x Round"), "B"]
s1_mod1_se_statusround = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Status x Round"), "SE"]
s1_mod1_t_statusround = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Status x Round"), "t-value"]
s1_mod1_p_statusround = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Status x Round"), "p-value"]
s1_mod1_CI_statusround = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Status x Round"), "95% CI"]

s1_mod1_beta_generositystatus = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate x Status"), "B"]
s1_mod1_se_generositystatus = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate x Status"), "SE"]
s1_mod1_t_generositystatus = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate x Status"), "t-value"]
s1_mod1_p_generositystatus = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate x Status"), "p-value"]
s1_mod1_CI_generositystatus = s1_mod1_statstable[which(s1_mod1_statstable$Predictor=="Reciprocity rate x Status"), "95% CI"]
```
```{r, include=FALSE, echo=FALSE, warning=FALSE}
# Simple slopes for status and generosity interaction

s1_mod1_beta_generosity_lowstatus = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='LowStatus'), "B"]
s1_mod1_se_generosity_lowstatus = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='LowStatus'), "SE"]
s1_mod1_t_generosity_lowstatus = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='LowStatus'), "t-value"]
s1_mod1_p_generosity_lowstatus = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='LowStatus'), "p-value"]
s1_mod1_CI_generosity_lowstatus = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='LowStatus'), "95% CI"]

s1_mod1_beta_generosity_highstatus = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='HighStatus'), "B"]
s1_mod1_se_generosity_highstatus = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='HighStatus'), "SE"]
s1_mod1_t_generosity_highstatus = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='HighStatus'), "t-value"]
s1_mod1_p_generosity_highstatus = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='HighStatus'), "p-value"]
s1_mod1_CI_generosity_highstatus = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='HighStatus'), "95% CI"]

s1_mod1_beta_status_greedy = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Greedy'), "B"]
s1_mod1_se_status_greedy = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Greedy'), "SE"]
s1_mod1_t_status_greedy = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Greedy'), "t-value"]
s1_mod1_p_status_greedy = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Greedy'), "p-value"]
s1_mod1_CI_status_greedy = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Greedy'), "95% CI"]

s1_mod1_beta_status_neutral = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Neutral'), "B"]
s1_mod1_se_status_neutral = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Neutral'), "SE"]
s1_mod1_t_status_neutral = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Neutral'), "t-value"]
s1_mod1_p_status_neutral = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Neutral'), "p-value"]
s1_mod1_CI_status_neutral = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Neutral'), "95% CI"]

s1_mod1_beta_status_generous = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Generous'), "B"]
s1_mod1_se_status_generous = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Generous'), "SE"]
s1_mod1_t_status_generous = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Generous'), "t-value"]
s1_mod1_p_status_generous = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Generous'), "p-value"]
s1_mod1_CI_status_generous = s1_mod1_sigslopes1[which(s1_mod1_sigslopes1$Reference=='Generous'), "95% CI"]
```
```{r, include=FALSE, echo=FALSE, warning=FALSE}
# Simple slopes for status and round interaction

s1_mod1_beta_status_firstround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='FirstRound'), "B"]
s1_mod1_se_status_firstround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='FirstRound'), "SE"]
s1_mod1_t_status_firstround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='FirstRound'), "t-value"]
s1_mod1_p_status_firstround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='FirstRound'), "p-value"]
s1_mod1_CI_status_firstround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='FirstRound'), "95% CI"]

s1_mod1_beta_status_middleround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='MiddleRound'), "B"]
s1_mod1_se_status_middleround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='MiddleRound'), "SE"]
s1_mod1_t_status_middleround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='MiddleRound'), "t-value"]
s1_mod1_p_status_middleround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='MiddleRound'), "p-value"]
s1_mod1_CI_status_middleround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='MiddleRound'), "95% CI"]

s1_mod1_beta_status_lastround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='LastRound'), "B"]
s1_mod1_se_status_lastround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='LastRound'), "SE"]
s1_mod1_t_status_lastround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='LastRound'), "t-value"]
s1_mod1_p_status_lastround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='LastRound'), "p-value"]
s1_mod1_CI_status_lastround = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='LastRound'), "95% CI"]

s1_mod1_beta_round_lowstatus = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='LowStatus'), "B"]
s1_mod1_se_round_lowstatus = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='LowStatus'), "SE"]
s1_mod1_t_round_lowstatus = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='LowStatus'), "t-value"]
s1_mod1_p_round_lowstatus = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='LowStatus'), "p-value"]
s1_mod1_CI_round_lowstatus = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='LowStatus'), "95% CI"]

s1_mod1_beta_round_highstatus = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='HighStatus'), "B"]
s1_mod1_se_round_highstatus = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='HighStatus'), "SE"]
s1_mod1_t_round_highstatus = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='HighStatus'), "t-value"]
s1_mod1_p_round_highstatus = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='HighStatus'), "p-value"]
s1_mod1_CI_round_highstatus = s1_mod1_sigslopes2[which(s1_mod1_sigslopes2$Reference=='HighStatus'), "95% CI"]
```
```{r, include=FALSE, echo=FALSE, warning=FALSE}
# Simple slopes for generosity and round interaction

s1_mod1_beta_generosity_firstround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='FirstRound'), "B"]
s1_mod1_se_generosity_firstround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='FirstRound'), "SE"]
s1_mod1_t_generosity_firstround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='FirstRound'), "t-value"]
s1_mod1_p_generosity_firstround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='FirstRound'), "p-value"]
s1_mod1_CI_generosity_firstround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='FirstRound'), "95% CI"]

s1_mod1_beta_generosity_middleround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='MiddleRound'), "B"]
s1_mod1_se_generosity_middleround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='MiddleRound'), "SE"]
s1_mod1_t_generosity_middleround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='MiddleRound'), "t-value"]
s1_mod1_p_generosity_middleround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='MiddleRound'), "p-value"]
s1_mod1_CI_generosity_middleround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='MiddleRound'), "95% CI"]

s1_mod1_beta_generosity_lastround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='LastRound'), "B"]
s1_mod1_se_generosity_lastround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='LastRound'), "SE"]
s1_mod1_t_generosity_lastround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='LastRound'), "t-value"]
s1_mod1_p_generosity_lastround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='LastRound'), "p-value"]
s1_mod1_CI_generosity_lastround = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='LastRound'), "95% CI"]

s1_mod1_beta_round_greedy = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Greedy'), "B"]
s1_mod1_se_round_greedy = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Greedy'), "SE"]
s1_mod1_t_round_greedy = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Greedy'), "t-value"]
s1_mod1_p_round_greedy = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Greedy'), "p-value"]
s1_mod1_CI_round_greedy = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Greedy'), "95% CI"]

s1_mod1_beta_round_neutral = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Neutral'), "B"]
s1_mod1_se_round_neutral = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Neutral'), "SE"]
s1_mod1_t_round_neutral = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Neutral'), "t-value"]
s1_mod1_p_round_neutral = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Neutral'), "p-value"]
s1_mod1_CI_round_neutral = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Neutral'), "95% CI"]

s1_mod1_beta_round_generous = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Generous'), "B"]
s1_mod1_se_round_generous = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Generous'), "SE"]
s1_mod1_t_round_generous = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Generous'), "t-value"]
s1_mod1_p_round_generous = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Generous'), "p-value"]
s1_mod1_CI_round_generous = s1_mod1_sigslopes3[which(s1_mod1_sigslopes3$Reference=='Generous'), "95% CI"]
```

Results from our second model yielded three significant main effects - of generosity (B = `r s1_mod1_beta_generosity`, SE = `r s1_mod1_se_generosity`, t = `r s1_mod1_t_generosity`, p = `r s1_mod1_p_generosity`, CI = `r s1_mod1_CI_generosity`), status (B = `r s1_mod1_beta_status`, SE = `r s1_mod1_se_status`, t = `r s1_mod1_t_status`, p = `r s1_mod1_p_status`, CI = `r s1_mod1_CI_status`), and round (B = `r s1_mod1_beta_round`, SE = `r s1_mod1_se_round`, t = `r s1_mod1_t_round`, p = `r s1_mod1_p_round`, CI = `r s1_mod1_CI_round`) - all of which were qualified by interactions. We found a significant interaction between generosity and round (B = `r s1_mod1_beta_generosityround`, SE = `r s1_mod1_se_generosityround`, t = `r s1_mod1_t_generosityround`, p = `r s1_mod1_p_generosityround`, CI = `r s1_mod1_CI_generosityround`), another between status and round (B = `r s1_mod1_beta_statusround`, SE = `r s1_mod1_se_statusround`, t = `r s1_mod1_t_statusround`, p = `r s1_mod1_p_statusround`, CI = `r s1_mod1_CI_statusround`), and a third between generosity and status (B = `r s1_mod1_beta_generositystatus`, SE = `r s1_mod1_se_generositystatus`, t = `r s1_mod1_t_generositystatus`, p = `r s1_mod1_p_generositystatus`, CI = `r s1_mod1_CI_generositystatus`). 

Participants decreased in their trust over rounds, but this decrease was greater for high status partners (B = `r s1_mod1_beta_round_highstatus`, SE = `r s1_mod1_se_round_highstatus`, t = `r s1_mod1_t_round_highstatus`, p = `r s1_mod1_p_round_highstatus`, CI = `r s1_mod1_CI_round_highstatus`) than for low status partners (B = `r s1_mod1_beta_round_lowstatus`, SE = `r s1_mod1_se_round_lowstatus`, t = `r s1_mod1_t_round_lowstatus`, p = `r s1_mod1_p_round_lowstatus`, CI = `r s1_mod1_CI_round_lowstatus`). This difference was due to greater trust for high status players compared to low status players in initial rounds.

Trust also decreased over rounds for generous (B = `r s1_mod1_beta_round_generous`, SE = `r s1_mod1_se_round_generous`, t = `r s1_mod1_t_round_generous`, p = `r s1_mod1_p_round_generous`, CI = `r s1_mod1_CI_round_generous`), neutral (B = `r s1_mod1_beta_round_neutral`, SE = `r s1_mod1_se_round_neutral`, t = `r s1_mod1_t_round_neutral`, p = `r s1_mod1_p_round_neutral`, CI = `r s1_mod1_CI_round_neutral`), and greedy players (B = `r s1_mod1_beta_round_greedy`, SE = `r s1_mod1_se_round_greedy`, t = `r s1_mod1_t_round_greedy`, p = `r s1_mod1_p_round_greedy`, CI = `r s1_mod1_CI_round_greedy`). Additionally, trust was greater for generous than neutral or greedy partners at the first (B = `r s1_mod1_beta_generosity_firstround`, SE = `r s1_mod1_se_generosity_firstround`, t = `r s1_mod1_t_generosity_firstround`, p = `r s1_mod1_p_generosity_firstround`, CI = `r s1_mod1_CI_generosity_firstround`), fifth (B = `r s1_mod1_beta_generosity_middleround`, SE = `r s1_mod1_se_generosity_middleround`, t = `r s1_mod1_t_generosity_middleround`, p = `r s1_mod1_p_generosity_middleround`, CI = `r s1_mod1_CI_generosity_middleround`), and tenth round (B = `r s1_mod1_beta_generosity_lastround`, SE = `r s1_mod1_se_generosity_lastround`, t = `r s1_mod1_t_generosity_lastround`, p = `r s1_mod1_p_generosity_lastround`, CI = `r s1_mod1_CI_generosity_lastround`). Taken together, these two results suggest that trust decreased over rounds, but this decrease was alleviated when participants noticed an actual difference in sharing behavior from their partner. In the case of status, which did not modulate partner return, participants trusted both high and low status partners similarly by the last round. But in the case of generosity, which was reflected in partner returns, participants continued to trust generous partners highly until the last round.

Finally, a simple slopes analysis of our generosity and status interaction revealed that participants were more likely to trust generous compared to neutral and greedy partners at both high (B = `r s1_mod1_beta_generosity_highstatus`, SE = `r s1_mod1_se_generosity_highstatus`, t = `r s1_mod1_t_generosity_highstatus`, p = `r s1_mod1_p_generosity_highstatus`, CI = `r s1_mod1_CI_generosity_highstatus`) and low status (B = `r s1_mod1_beta_generosity_lowstatus`, SE = `r s1_mod1_se_generosity_lowstatus`, t = `r s1_mod1_t_generosity_lowstatus`, p = `r s1_mod1_p_generosity_lowstatus`, CI = `r s1_mod1_CI_generosity_lowstatus`). They were also more likely to trust high status partners more than low status partners for greedy (B = `r s1_mod1_beta_status_greedy`, SE = `r s1_mod1_se_status_greedy`, t = `r s1_mod1_t_status_greedy`, p = `r s1_mod1_p_status_greedy`, CI = `r s1_mod1_CI_status_greedy`), neutral (B = `r s1_mod1_beta_status_neutral`, SE = `r s1_mod1_se_status_neutral`, t = `r s1_mod1_t_status_neutral`, p = `r s1_mod1_p_status_neutral`, CI = `r s1_mod1_CI_status_neutral`), and generous partners (B = `r s1_mod1_beta_status_generous`, SE = `r s1_mod1_se_status_generous`, t = `r s1_mod1_t_status_generous`, p = `r s1_mod1_p_status_generous`, CI = `r s1_mod1_CI_status_generous`).

However, we again failed to find any significant effects - main or in interactions - of agency.

Taken together, results from our first study showed that people attend to competency status and reciprocity when making trust decisions with humans and AI. They reliably infer reciprocity profiles for AI, suggesting that participants mentalize AI and learn their "traits." 

Unexpectedly, there was little difference in how participants trusted humans vs how they trusted AI. This could be a true negative - maybe we do treat humans and AI similarly when deciding whom to trust. Or it could be due to our design - "AI" is not the automatic "other" category for "human." Because our design was between-subjects for the agency factor, participants who played with "human" players probably couldn't guess that they were supposed to compare their human partners to a possible AI partner. To ensure that this was in fact a true negative, we ran a completely within-subjects second study with a nearly-identical procedure - instead of 6 games, participants played 12 games, 6 with humans and 6 with AI.

## Model 2

```{r, include=FALSE, echo=FALSE, warning=FALSE}
s1_mod2_beta_status = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Status"), "B"]
s1_mod2_se_status = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Status"), "SE"]
s1_mod2_t_status = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Status"), "t-value"]
s1_mod2_p_status = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Status"), "p-value"]
s1_mod2_CI_status = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Status"), "95% CI"]

s1_mod2_beta_generosity = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Reciprocity rate"), "B"]
s1_mod2_se_generosity = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Reciprocity rate"), "SE"]
s1_mod2_t_generosity = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Reciprocity rate"), "t-value"]
s1_mod2_p_generosity = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Reciprocity rate"), "p-value"]
s1_mod2_CI_generosity = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Reciprocity rate"), "95% CI"]

s1_mod2_beta_feedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Feedback"), "B"]
s1_mod2_se_feedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Feedback"), "SE"]
s1_mod2_t_feedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Feedback"), "t-value"]
s1_mod2_p_feedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Feedback"), "p-value"]
s1_mod2_CI_feedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Feedback"), "95% CI"]

s1_mod2_beta_agencygenerosity = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Agency x Reciprocity rate"), "B"]
s1_mod2_se_agencygenerosity = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Agency x Reciprocity rate"), "SE"]
s1_mod2_t_agencygenerosity = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Agency x Reciprocity rate"), "t-value"]
s1_mod2_p_agencygenerosity = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Agency x Reciprocity rate"), "p-value"]
s1_mod2_CI_agencygenerosity = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Agency x Reciprocity rate"), "95% CI"]
  
s1_mod2_beta_statusfeedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Status x Feedback"), "B"]
s1_mod2_se_statusfeedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Status x Feedback"), "SE"]
s1_mod2_t_statusfeedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Status x Feedback"), "t-value"]
s1_mod2_p_statusfeedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Status x Feedback"), "p-value"]
s1_mod2_CI_statusfeedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Status x Feedback"), "95% CI"]
  
s1_mod2_beta_generosityfeedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Reciprocity rate x Feedback"), "B"]
s1_mod2_se_generosityfeedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Reciprocity rate x Feedback"), "SE"]
s1_mod2_t_generosityfeedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Reciprocity rate x Feedback"), "t-value"]
s1_mod2_p_generosityfeedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Reciprocity rate x Feedback"), "p-value"]
s1_mod2_CI_generosityfeedback = s1_mod2_statstable[which(s1_mod2_statstable$Predictor=="Reciprocity rate x Feedback"), "95% CI"]
```
```{r, include=FALSE, echo=FALSE, warning=FALSE}
# Simple slopes for agency and generosity interaction

s1_mod2_beta_generosity_human = s1_mod2_sigslopes1[which(s1_mod2_sigslopes1$Reference=='Human'), "B"]
s1_mod2_se_generosity_human = s1_mod2_sigslopes1[which(s1_mod2_sigslopes1$Reference=='Human'), "SE"]
s1_mod2_t_generosity_human = s1_mod2_sigslopes1[which(s1_mod2_sigslopes1$Reference=='Human'), "t-value"]
s1_mod2_p_generosity_human = s1_mod2_sigslopes1[which(s1_mod2_sigslopes1$Reference=='Human'), "p-value"]
s1_mod2_CI_generosity_human = s1_mod2_sigslopes1[which(s1_mod2_sigslopes1$Reference=='Human'), "95% CI"]

s1_mod2_beta_generosity_ai = s1_mod2_sigslopes1[which(s1_mod2_sigslopes1$Reference=='AI'), "B"]
s1_mod2_se_generosity_ai = s1_mod2_sigslopes1[which(s1_mod2_sigslopes1$Reference=='AI'), "SE"]
s1_mod2_t_generosity_ai = s1_mod2_sigslopes1[which(s1_mod2_sigslopes1$Reference=='AI'), "t-value"]
s1_mod2_p_generosity_ai = s1_mod2_sigslopes1[which(s1_mod2_sigslopes1$Reference=='AI'), "p-value"]
s1_mod2_CI_generosity_ai = s1_mod2_sigslopes1[which(s1_mod2_sigslopes1$Reference=='AI'), "95% CI"]
```
```{r, include=FALSE, echo=FALSE, warning=FALSE}
# Simple slopes for status and feedback interaction

s1_mod2_beta_feedback_lowstatus = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='LowStatus'), "B"]
s1_mod2_se_feedback_lowstatus = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='LowStatus'), "SE"]
s1_mod2_t_feedback_lowstatus = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='LowStatus'), "t-value"]
s1_mod2_p_feedback_lowstatus = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='LowStatus'), "p-value"]
s1_mod2_CI_feedback_lowstatus = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='LowStatus'), "95% CI"]

s1_mod2_beta_feedback_highstatus = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='HighStatus'), "B"]
s1_mod2_se_feedback_highstatus = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='HighStatus'), "SE"]
s1_mod2_t_feedback_highstatus = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='HighStatus'), "t-value"]
s1_mod2_p_feedback_highstatus = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='HighStatus'), "p-value"]
s1_mod2_CI_feedback_highstatus = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='HighStatus'), "95% CI"]

s1_mod2_beta_status_lowfeedback = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='LowFeedback'), "B"]
s1_mod2_se_status_lowfeedback = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='HighStatus'), "SE"]
s1_mod2_t_status_lowfeedback = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='HighStatus'), "t-value"]
s1_mod2_p_status_lowfeedback = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='HighStatus'), "p-value"]
s1_mod2_CI_status_lowfeedback = s1_mod2_sigslopes2[which(s1_mod2_sigslopes2$Reference=='HighStatus'), "95% CI"]
```
```{r, include=FALSE, echo=FALSE, warning=FALSE}
# Simple slopes for generosity and feedback interaction

s1_mod2_beta_feedback_greedy = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Greedy'), "B"]
s1_mod2_se_feedback_greedy = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Greedy'), "SE"]
s1_mod2_t_feedback_greedy = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Greedy'), "t-value"]
s1_mod2_p_feedback_greedy = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Greedy'), "p-value"]
s1_mod2_CI_feedback_greedy = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Greedy'), "95% CI"]

s1_mod2_beta_feedback_neutral = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Neutral'), "B"]
s1_mod2_se_feedback_neutral = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Neutral'), "SE"]
s1_mod2_t_feedback_neutral = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Neutral'), "t-value"]
s1_mod2_p_feedback_neutral = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Neutral'), "p-value"]
s1_mod2_CI_feedback_neutral = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Neutral'), "95% CI"]

s1_mod2_beta_feedback_generous = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Generous'), "B"]
s1_mod2_se_feedback_generous = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Generous'), "SE"]
s1_mod2_t_feedback_generous = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Generous'), "t-value"]
s1_mod2_p_feedback_generous = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Generous'), "p-value"]
s1_mod2_CI_feedback_generous = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='Generous'), "95% CI"]

s1_mod2_beta_generosity_lowfeedback = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='LowFeedback'), "B"]
s1_mod2_se_generosity_lowfeedback = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='LowFeedback'), "SE"]
s1_mod2_t_generosity_lowfeedback = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='LowFeedback'), "t-value"]
s1_mod2_p_generosity_lowfeedback = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='LowFeedback'), "p-value"]
s1_mod2_CI_generosity_lowfeedback = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='LowFeedback'), "95% CI"]

s1_mod2_beta_generosity_midfeedback = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='MidFeedback'), "B"]
s1_mod2_se_generosity_midfeedback = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='MidFeedback'), "SE"]
s1_mod2_t_generosity_midfeedback = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='MidFeedback'), "t-value"]
s1_mod2_p_generosity_midfeedback = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='MidFeedback'), "p-value"]
s1_mod2_CI_generosity_midfeedback = s1_mod2_sigslopes3[which(s1_mod2_sigslopes3$Reference=='MidFeedback'), "95% CI"]
```

Results from our second model showed significant main effects of status (B = `r s1_mod2_beta_status`, SE = `r s1_mod2_se_status`, t = `r s1_mod2_t_status`, p = `r s1_mod2_p_status`, CI = `r s1_mod2_CI_status`), generosity (B = `r s1_mod2_beta_generosity`, SE = `r s1_mod2_se_generosity`, t = `r s1_mod2_t_generosity`, p = `r s1_mod2_p_generosity`, CI = `r s1_mod2_CI_generosity`), and feedback (B = `r s1_mod2_beta_feedback`, SE = `r s1_mod2_se_feedback`, t = `r s1_mod2_t_feedback`, p = `r s1_mod2_p_feedback`, CI = `r s1_mod2_CI_feedback`), which were qualified by a status & feedback interaction (B = `r s1_mod2_beta_statusfeedback`, SE = `r s1_mod2_se_statusfeedback`, t = `r s1_mod2_t_statusfeedback`, p = `r s1_mod2_p_statusfeedback`, CI = `r s1_mod2_CI_statusfeedback`), and a generosity & feedback interaction (B = `r s1_mod2_beta_generosityfeedback`, SE = `r s1_mod2_se_generosityfeedback`, t = `r s1_mod2_t_generosityfeedback`, p = `r s1_mod2_p_generosityfeedback`, CI = `r s1_mod2_CI_generosityfeedback`). 

Increase in feedback led to increase in trust towards both low (B = `r s1_mod2_beta_feedback_lowstatus`, SE = `r s1_mod2_se_feedback_lowstatus`, t = `r s1_mod2_t_feedback_lowstatus`, p = `r s1_mod2_p_feedback_lowstatus`, CI = `r s1_mod2_CI_feedback_lowstatus`) and high status partners (B = `r s1_mod2_beta_feedback_highstatus`, SE = `r s1_mod2_se_feedback_highstatus`, t = `r s1_mod2_t_feedback_highstatus`, p = `r s1_mod2_p_feedback_highstatus`, CI = `r s1_mod2_CI_feedback_highstatus`). However, while high status partners were trusted more than low status partners at a low feedback level (centered at 0; B = `r s1_mod2_beta_status_lowfeedback`, SE = `r s1_mod2_se_status_lowfeedback`, t = `r s1_mod2_t_status_lowfeedback`, p = `r s1_mod2_p_status_lowfeedback`, CI = `r s1_mod2_CI_status_lowfeedback`), the difference between high and low status partners at medium (centered at 11) and high (centered at 22) feedback levels was insignificant. 

Similarly, increase in feedback led to increase in trust towards generous (B = `r s1_mod2_beta_feedback_generous`, SE = `r s1_mod2_se_feedback_generous`, t = `r s1_mod2_t_feedback_generous`, p = `r s1_mod2_p_feedback_generous`, CI = `r s1_mod2_CI_feedback_generous`), neutral (B = `r s1_mod2_beta_feedback_neutral`, SE = `r s1_mod2_se_feedback_neutral`, t = `r s1_mod2_t_feedback_neutral`, p = `r s1_mod2_p_feedback_neutral`, CI = `r s1_mod2_CI_feedback_neutral`), and greedy partners (B = `r s1_mod2_beta_feedback_greedy`, SE = `r s1_mod2_se_feedback_greedy`, t = `r s1_mod2_t_feedback_greedy`, p = `r s1_mod2_p_feedback_greedy`, CI = `r s1_mod2_CI_feedback_greedy`). However, difference between trust towards generous, neutral, and greedy partners decreased as feedback increased -- at low (centered at 0; B = `r s1_mod2_beta_generosity_lowfeedback`, SE = `r s1_mod2_se_generosity_lowfeedback`, t = `r s1_mod2_t_generosity_lowfeedback`, p = `r s1_mod2_p_generosity_lowfeedback`, CI = `r s1_mod2_CI_generosity_lowfeedback`) and medium (centered at 11; B = `r s1_mod2_beta_generosity_midfeedback`, SE = `r s1_mod2_se_generosity_midfeedback`, t = `r s1_mod2_t_generosity_midfeedback`, p = `r s1_mod2_p_generosity_midfeedback`, CI = `r s1_mod2_CI_generosity_midfeedback`) feedback, generous partners were trusted more than neutral and greedy partners, but by high (centered at 22) feedback this difference in trust by generosity level became insignificant.

While there were no main effects of agency, we did find an agency and generosity interaction (B = `r s1_mod2_beta_agencygenerosity`, SE = `r s1_mod2_se_agencygenerosity`, t = `r s1_mod2_t_agencygenerosity`, p = `r s1_mod2_p_agencygenerosity`, CI = `r s1_mod2_CI_agencygenerosity`). However, this interaction was entirely driven by generosity - participants trusted generous partners more than neutral and greedy partners for both human (B = `r s1_mod2_beta_generosity_human`, SE = `r s1_mod2_se_generosity_human`, t = `r s1_mod2_t_generosity_human`, p = `r s1_mod2_p_generosity_human`, CI = `r s1_mod2_CI_generosity_human`) and AI partners (B = `r s1_mod2_beta_generosity_ai`, SE = `r s1_mod2_se_generosity_ai`, t = `r s1_mod2_t_generosity_ai`, p = `r s1_mod2_p_generosity_ai`, CI = `r s1_mod2_CI_generosity_ai`), but we did not find any simple differences by agency.

Taken together, these results show that status, generosity, and feedback impact trust decisions. Specifically, higher feedback and greater generosity lead to higher trust, while higher status led to higher trust only when feedback was low. However, we did not find any significant effects of agency, nor the expected four-way interaction between agency, generosity, status, and feedback. 

# Study 2

Study 2 was a within-subjects design with four factors -- agency (human, AI), status (high, low), generosity (greedy, neutral, generous), and feedback (9 rounds).

## Model 1

```{r, include=FALSE, echo=FALSE, warning=FALSE}
s2_mod1_beta_generosity = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Reciprocity rate"), "B"]
s2_mod1_se_generosity = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Reciprocity rate"), "SE"]
s2_mod1_t_generosity = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Reciprocity rate"), "t-value"]
s2_mod1_p_generosity = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Reciprocity rate"), "p-value"]
s2_mod1_CI_generosity = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Reciprocity rate"), "95% CI"]

s2_mod1_beta_agency = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Agency"), "B"]
s2_mod1_se_agency = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Agency"), "SE"]
s2_mod1_t_agency = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Agency"), "t-value"]
s2_mod1_p_agency = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Agency"), "p-value"]
s2_mod1_CI_agency = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Agency"), "95% CI"]

s2_mod1_beta_status = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Status"), "B"]
s2_mod1_se_status = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Status"), "SE"]
s2_mod1_t_status = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Status"), "t-value"]
s2_mod1_p_status = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Status"), "p-value"]
s2_mod1_CI_status = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Status"), "95% CI"]

s2_mod1_beta_round = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Round"), "B"]
s2_mod1_se_round = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Round"), "SE"]
s2_mod1_t_round = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Round"), "t-value"]
s2_mod1_p_round = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Round"), "p-value"]
s2_mod1_CI_round = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Round"), "95% CI"]

s2_mod1_beta_agencystatusgenerosityround = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Agency x Reciprocity rate x Status x Round"), "B"]
s2_mod1_se_agencystatusgenerosityround = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Agency x Reciprocity rate x Status x Round"), "SE"]
s2_mod1_t_agencystatusgenerosityround = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Agency x Reciprocity rate x Status x Round"), "t-value"]
s2_mod1_p_agencystatusgenerosityround = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Agency x Reciprocity rate x Status x Round"), "p-value"]
s2_mod1_CI_agencystatusgenerosityround = s2_mod1_statstable[which(s2_mod1_statstable$Predictor=="Agency x Reciprocity rate x Status x Round"), "95% CI"]
```
```{r, include=FALSE, echo=FALSE}
# Simple slopes for agency, status, generosity, and round interaction
# Round
s2_mod1_beta_round_lowstatusgreedyai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Greedy'), "B"]
s2_mod1_se_round_lowstatusgreedyai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Greedy'), "SE"]
s2_mod1_t_round_lowstatusgreedyai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Greedy'), "t-value"]
s2_mod1_p_round_lowstatusgreedyai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Greedy'), "p-value"]
s2_mod1_CI_round_lowstatusgreedyai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Greedy'), "95% CI"]

s2_mod1_beta_round_lowstatusneutralai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Neutral'), "B"]
s2_mod1_se_round_lowstatusneutralai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Neutral'), "SE"]
s2_mod1_t_round_lowstatusneutralai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Neutral'), "t-value"]
s2_mod1_p_round_lowstatusneutralai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Neutral'), "p-value"]
s2_mod1_CI_round_lowstatusneutralai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Neutral'), "95% CI"]

s2_mod1_beta_round_lowstatusgenerousai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Generous'), "B"]
s2_mod1_se_round_lowstatusgenerousai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Generous'), "SE"]
s2_mod1_t_round_lowstatusgenerousai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Generous'), "t-value"]
s2_mod1_p_round_lowstatusgenerousai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Generous'), "p-value"]
s2_mod1_CI_round_lowstatusgenerousai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Generous'), "95% CI"]

s2_mod1_beta_round_highstatusgreedyai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Greedy'), "B"]
s2_mod1_se_round_highstatusgreedyai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Greedy'), "SE"]
s2_mod1_t_round_highstatusgreedyai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Greedy'), "t-value"]
s2_mod1_p_round_highstatusgreedyai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Greedy'), "p-value"]
s2_mod1_CI_round_highstatusgreedyai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Greedy'), "95% CI"]

s2_mod1_beta_round_highstatusneutralai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Neutral'), "B"]
s2_mod1_se_round_highstatusneutralai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Neutral'), "SE"]
s2_mod1_t_round_highstatusneutralai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Neutral'), "t-value"]
s2_mod1_p_round_highstatusneutralai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Neutral'), "p-value"]
s2_mod1_CI_round_highstatusneutralai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Neutral'), "95% CI"]

s2_mod1_beta_round_highstatusgenerousai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Generous'), "B"]
s2_mod1_se_round_highstatusgenerousai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Generous'), "SE"]
s2_mod1_t_round_highstatusgenerousai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Generous'), "t-value"]
s2_mod1_p_round_highstatusgenerousai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Generous'), "p-value"]
s2_mod1_CI_round_highstatusgenerousai = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Generous'), "95% CI"]

s2_mod1_beta_round_lowstatusgreedyhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Greedy'), "B"]
s2_mod1_se_round_lowstatusgreedyhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Greedy'), "SE"]
s2_mod1_t_round_lowstatusgreedyhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Greedy'), "t-value"]
s2_mod1_p_round_lowstatusgreedyhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Greedy'), "p-value"]
s2_mod1_CI_round_lowstatusgreedyhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Greedy'), "95% CI"]

s2_mod1_beta_round_lowstatusneutralhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Neutral'), "B"]
s2_mod1_se_round_lowstatusneutralhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Neutral'), "SE"]
s2_mod1_t_round_lowstatusneutralhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Neutral'), "t-value"]
s2_mod1_p_round_lowstatusneutralhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Neutral'), "p-value"]
s2_mod1_CI_round_lowstatusneutralhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Neutral'), "95% CI"]

s2_mod1_beta_round_lowstatusgeneroushuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Generous'), "B"]
s2_mod1_se_round_lowstatusgeneroushuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Generous'), "SE"]
s2_mod1_t_round_lowstatusgeneroushuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Generous'), "t-value"]
s2_mod1_p_round_lowstatusgeneroushuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Generous'), "p-value"]
s2_mod1_CI_round_lowstatusgeneroushuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Generous'), "95% CI"]

s2_mod1_beta_round_highstatusgreedyhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Greedy'), "B"]
s2_mod1_se_round_highstatusgreedyhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Greedy'), "SE"]
s2_mod1_t_round_highstatusgreedyhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Greedy'), "t-value"]
s2_mod1_p_round_highstatusgreedyhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Greedy'), "p-value"]
s2_mod1_CI_round_highstatusgreedyhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Greedy'), "95% CI"]

s2_mod1_beta_round_highstatusneutralhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Neutral'), "B"]
s2_mod1_se_round_highstatusneutralhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Neutral'), "SE"]
s2_mod1_t_round_highstatusneutralhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Neutral'), "t-value"]
s2_mod1_p_round_highstatusneutralhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Neutral'), "p-value"]
s2_mod1_CI_round_highstatusneutralhuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Neutral'), "95% CI"]

s2_mod1_beta_round_highstatusgeneroushuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Generous'), "B"]
s2_mod1_se_round_highstatusgeneroushuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Generous'), "SE"]
s2_mod1_t_round_highstatusgeneroushuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Generous'), "t-value"]
s2_mod1_p_round_highstatusgeneroushuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Generous'), "p-value"]
s2_mod1_CI_round_highstatusgeneroushuman = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Generous'), "95% CI"]

# Generosity
s2_mod1_beta_generosity_ailowstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_FirstRound'), "B"]
s2_mod1_se_generosity_ailowstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_FirstRound'), "SE"]
s2_mod1_t_generosity_ailowstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_FirstRound'), "t-value"]
s2_mod1_p_generosity_ailowstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_FirstRound'), "p-value"]
s2_mod1_CI_generosity_ailowstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_FirstRound'), "95% CI"]

s2_mod1_beta_generosity_ailowstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_MiddleRound'), "B"]
s2_mod1_se_generosity_ailowstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_MiddleRound'), "SE"]
s2_mod1_t_generosity_ailowstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_MiddleRound'), "t-value"]
s2_mod1_p_generosity_ailowstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_MiddleRound'), "p-value"]
s2_mod1_CI_generosity_ailowstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_generosity_ailowstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_LastRound'), "B"]
s2_mod1_se_generosity_ailowstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_LastRound'), "SE"]
s2_mod1_t_generosity_ailowstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_LastRound'), "t-value"]
s2_mod1_p_generosity_ailowstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_LastRound'), "p-value"]
s2_mod1_CI_generosity_ailowstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_LowStatus_Round_LastRound'), "95% CI"]

s2_mod1_beta_generosity_aihighstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_FirstRound'), "B"]
s2_mod1_se_generosity_aihighstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_FirstRound'), "SE"]
s2_mod1_t_generosity_aihighstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_FirstRound'), "t-value"]
s2_mod1_p_generosity_aihighstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_FirstRound'), "p-value"]
s2_mod1_CI_generosity_aihighstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_FirstRound'), "95% CI"]

s2_mod1_beta_generosity_aihighstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_MiddleRound'), "B"]
s2_mod1_se_generosity_aihighstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_MiddleRound'), "SE"]
s2_mod1_t_generosity_aihighstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_MiddleRound'), "t-value"]
s2_mod1_p_generosity_aihighstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_MiddleRound'), "p-value"]
s2_mod1_CI_generosity_aihighstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_generosity_aihighstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_LastRound'), "B"]
s2_mod1_se_generosity_aihighstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_LastRound'), "SE"]
s2_mod1_t_generosity_aihighstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_LastRound'), "t-value"]
s2_mod1_p_generosity_aihighstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_LastRound'), "p-value"]
s2_mod1_CI_generosity_aihighstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_HighStatus_Round_LastRound'), "95% CI"]

s2_mod1_beta_generosity_humanlowstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_FirstRound'), "B"]
s2_mod1_se_generosity_humanlowstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_FirstRound'), "SE"]
s2_mod1_t_generosity_humanlowstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_FirstRound'), "t-value"]
s2_mod1_p_generosity_humanlowstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_FirstRound'), "p-value"]
s2_mod1_CI_generosity_humanlowstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_FirstRound'), "95% CI"]

s2_mod1_beta_generosity_humanlowstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_MiddleRound'), "B"]
s2_mod1_se_generosity_humanlowstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_MiddleRound'), "SE"]
s2_mod1_t_generosity_humanlowstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_MiddleRound'), "t-value"]
s2_mod1_p_generosity_humanlowstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_MiddleRound'), "p-value"]
s2_mod1_CI_generosity_humanlowstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_generosity_humanlowstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_LastRound'), "B"]
s2_mod1_se_generosity_humanlowstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_LastRound'), "SE"]
s2_mod1_t_generosity_humanlowstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_LastRound'), "t-value"]
s2_mod1_p_generosity_humanlowstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_LastRound'), "p-value"]
s2_mod1_CI_generosity_humanlowstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_LowStatus_Round_LastRound'), "95% CI"]

s2_mod1_beta_generosity_humanhighstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_FirstRound'), "B"]
s2_mod1_se_generosity_humanhighstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_FirstRound'), "SE"]
s2_mod1_t_generosity_humanhighstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_FirstRound'), "t-value"]
s2_mod1_p_generosity_humanhighstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_FirstRound'), "p-value"]
s2_mod1_CI_generosity_humanhighstatusfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_FirstRound'), "95% CI"]

s2_mod1_beta_generosity_humanhighstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_MiddleRound'), "B"]
s2_mod1_se_generosity_humanhighstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_MiddleRound'), "SE"]
s2_mod1_t_generosity_humanhighstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_MiddleRound'), "t-value"]
s2_mod1_p_generosity_humanhighstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_MiddleRound'), "p-value"]
s2_mod1_CI_generosity_humanhighstatusmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_generosity_humanhighstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_LastRound'), "B"]
s2_mod1_se_generosity_humanhighstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_LastRound'), "SE"]
s2_mod1_t_generosity_humanhighstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_LastRound'), "t-value"]
s2_mod1_p_generosity_humanhighstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_LastRound'), "p-value"]
s2_mod1_CI_generosity_humanhighstatuslastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_HighStatus_Round_LastRound'), "95% CI"]

# Agency
s2_mod1_beta_agency_lowstatusgreedyfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Greedy_Round_FirstRound'), "B"]
s2_mod1_se_agency_lowstatusgreedyfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Greedy_Round_FirstRound'), "SE"]
s2_mod1_t_agency_lowstatusgreedyfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Greedy_Round_FirstRound'), "t-value"]
s2_mod1_p_agency_lowstatusgreedyfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Greedy_Round_FirstRound'), "p-value"]
s2_mod1_CI_agency_lowstatusgreedyfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Greedy_Round_FirstRound'), "95% CI"]

s2_mod1_beta_agency_lowstatusneutralfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Neutral_Round_FirstRound'), "B"]
s2_mod1_se_agency_lowstatusneutralfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Neutral_Round_FirstRound'), "SE"]
s2_mod1_t_agency_lowstatusneutralfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Neutral_Round_FirstRound'), "t-value"]
s2_mod1_p_agency_lowstatusneutralfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Neutral_Round_FirstRound'), "p-value"]
s2_mod1_CI_agency_lowstatusneutralfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Neutral_Round_FirstRound'), "95% CI"]

s2_mod1_beta_agency_lowstatusgenerousfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Generous_Round_FirstRound'), "B"]
s2_mod1_se_agency_lowstatusgenerousfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Generous_Round_FirstRound'), "SE"]
s2_mod1_t_agency_lowstatusgenerousfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Generous_Round_FirstRound'), "t-value"]
s2_mod1_p_agency_lowstatusgenerousfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Generous_Round_FirstRound'), "p-value"]
s2_mod1_CI_agency_lowstatusgenerousfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Generous_Round_FirstRound'), "95% CI"]

s2_mod1_beta_agency_lowstatusgreedymiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Greedy_Round_MiddleRound'), "B"]
s2_mod1_se_agency_lowstatusgreedymiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Greedy_Round_MiddleRound'), "SE"]
s2_mod1_t_agency_lowstatusgreedymiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Greedy_Round_MiddleRound'), "t-value"]
s2_mod1_p_agency_lowstatusgreedymiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Greedy_Round_MiddleRound'), "p-value"]
s2_mod1_CI_agency_lowstatusgreedymiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Greedy_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_agency_lowstatusneutralmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Neutral_Round_MiddleRound'), "B"]
s2_mod1_se_agency_lowstatusneutralmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Neutral_Round_MiddleRound'), "SE"]
s2_mod1_t_agency_lowstatusneutralmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Neutral_Round_MiddleRound'), "t-value"]
s2_mod1_p_agency_lowstatusneutralmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Neutral_Round_MiddleRound'), "p-value"]
s2_mod1_CI_agency_lowstatusneutralmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Neutral_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_agency_lowstatusgenerousmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Generous_Round_MiddleRound'), "B"]
s2_mod1_se_agency_lowstatusgenerousmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Generous_Round_MiddleRound'), "SE"]
s2_mod1_t_agency_lowstatusgenerousmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Generous_Round_MiddleRound'), "t-value"]
s2_mod1_p_agency_lowstatusgenerousmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Generous_Round_MiddleRound'), "p-value"]
s2_mod1_CI_agency_lowstatusgenerousmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='LowStatus_Generous_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_agency_highstatusgreedyfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Greedy_Round_FirstRound'), "B"]
s2_mod1_se_agency_highstatusgreedyfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Greedy_Round_FirstRound'), "SE"]
s2_mod1_t_agency_highstatusgreedyfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Greedy_Round_FirstRound'), "t-value"]
s2_mod1_p_agency_highstatusgreedyfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Greedy_Round_FirstRound'), "p-value"]
s2_mod1_CI_agency_highstatusgreedyfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Greedy_Round_FirstRound'), "95% CI"]

s2_mod1_beta_agency_highstatusneutralfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Neutral_Round_FirstRound'), "B"]
s2_mod1_se_agency_highstatusneutralfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Neutral_Round_FirstRound'), "SE"]
s2_mod1_t_agency_highstatusneutralfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Neutral_Round_FirstRound'), "t-value"]
s2_mod1_p_agency_highstatusneutralfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Neutral_Round_FirstRound'), "p-value"]
s2_mod1_CI_agency_highstatusneutralfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Neutral_Round_FirstRound'), "95% CI"]

s2_mod1_beta_agency_highstatusgenerousfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Generous_Round_FirstRound'), "B"]
s2_mod1_se_agency_highstatusgenerousfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Generous_Round_FirstRound'), "SE"]
s2_mod1_t_agency_highstatusgenerousfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Generous_Round_FirstRound'), "t-value"]
s2_mod1_p_agency_highstatusgenerousfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Generous_Round_FirstRound'), "p-value"]
s2_mod1_CI_agency_highstatusgenerousfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Generous_Round_FirstRound'), "95% CI"]

s2_mod1_beta_agency_highstatusgreedymiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Greedy_Round_MiddleRound'), "B"]
s2_mod1_se_agency_highstatusgreedymiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Greedy_Round_MiddleRound'), "SE"]
s2_mod1_t_agency_highstatusgreedymiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Greedy_Round_MiddleRound'), "t-value"]
s2_mod1_p_agency_highstatusgreedymiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Greedy_Round_MiddleRound'), "p-value"]
s2_mod1_CI_agency_highstatusgreedymiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Greedy_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_agency_highstatusneutralmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Neutral_Round_MiddleRound'), "B"]
s2_mod1_se_agency_highstatusneutralmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Neutral_Round_MiddleRound'), "SE"]
s2_mod1_t_agency_highstatusneutralmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Neutral_Round_MiddleRound'), "t-value"]
s2_mod1_p_agency_highstatusneutralmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Neutral_Round_MiddleRound'), "p-value"]
s2_mod1_CI_agency_highstatusneutralmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Neutral_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_agency_highstatusgenerousmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Generous_Round_MiddleRound'), "B"]
s2_mod1_se_agency_highstatusgenerousmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Generous_Round_MiddleRound'), "SE"]
s2_mod1_t_agency_highstatusgenerousmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Generous_Round_MiddleRound'), "t-value"]
s2_mod1_p_agency_highstatusgenerousmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Generous_Round_MiddleRound'), "p-value"]
s2_mod1_CI_agency_highstatusgenerousmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='HighStatus_Generous_Round_MiddleRound'), "95% CI"]

# Status
s2_mod1_beta_status_greedyailastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Greedy_Round_LastRound'), "B"]
s2_mod1_se_status_greedyailastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Greedy_Round_LastRound'), "SE"]
s2_mod1_t_status_greedyailastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Greedy_Round_LastRound'), "t-value"]
s2_mod1_p_status_greedyailastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Greedy_Round_LastRound'), "p-value"]
s2_mod1_CI_status_greedyailastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Greedy_Round_LastRound'), "95% CI"]

s2_mod1_beta_status_greedyhumanmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Greedy_Round_MiddleRound'), "B"]
s2_mod1_se_status_greedyhumanmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Greedy_Round_MiddleRound'), "SE"]
s2_mod1_t_status_greedyhumanmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Greedy_Round_MiddleRound'), "t-value"]
s2_mod1_p_status_greedyhumanmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Greedy_Round_MiddleRound'), "p-value"]
s2_mod1_CI_status_greedyhumanmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Greedy_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_status_greedyhumanlastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Greedy_Round_LastRound'), "B"]
s2_mod1_se_status_greedyhumanlastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Greedy_Round_LastRound'), "SE"]
s2_mod1_t_status_greedyhumanlastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Greedy_Round_LastRound'), "t-value"]
s2_mod1_p_status_greedyhumanlastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Greedy_Round_LastRound'), "p-value"]
s2_mod1_CI_status_greedyhumanlastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Greedy_Round_LastRound'), "95% CI"]

s2_mod1_beta_status_neutralaifirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Neutral_Round_FirstRound'), "B"]
s2_mod1_se_status_neutralaifirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Neutral_Round_FirstRound'), "SE"]
s2_mod1_t_status_neutralaifirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Neutral_Round_FirstRound'), "t-value"]
s2_mod1_p_status_neutralaifirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Neutral_Round_FirstRound'), "p-value"]
s2_mod1_CI_status_neutralaifirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Neutral_Round_FirstRound'), "95% CI"]

s2_mod1_beta_status_neutralaimiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Neutral_Round_MiddleRound'), "B"]
s2_mod1_se_status_neutralaimiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Neutral_Round_MiddleRound'), "SE"]
s2_mod1_t_status_neutralaimiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Neutral_Round_MiddleRound'), "t-value"]
s2_mod1_p_status_neutralaimiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Neutral_Round_MiddleRound'), "p-value"]
s2_mod1_CI_status_neutralaimiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Neutral_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_status_neutralhumanfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Neutral_Round_FirstRound'), "B"]
s2_mod1_se_status_neutralhumanfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Neutral_Round_FirstRound'), "SE"]
s2_mod1_t_status_neutralhumanfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Neutral_Round_FirstRound'), "t-value"]
s2_mod1_p_status_neutralhumanfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Neutral_Round_FirstRound'), "p-value"]
s2_mod1_CI_status_neutralhumanfirstround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Neutral_Round_FirstRound'), "95% CI"]

s2_mod1_beta_status_generousaimiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Generous_Round_MiddleRound'), "B"]
s2_mod1_se_status_generousaimiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Generous_Round_MiddleRound'), "SE"]
s2_mod1_t_status_generousaimiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Generous_Round_MiddleRound'), "t-value"]
s2_mod1_p_status_generousaimiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Generous_Round_MiddleRound'), "p-value"]
s2_mod1_CI_status_generousaimiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Generous_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_status_generousailastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Generous_Round_LastRound'), "B"]
s2_mod1_se_status_generousailastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Generous_Round_LastRound'), "SE"]
s2_mod1_t_status_generousailastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Generous_Round_LastRound'), "t-value"]
s2_mod1_p_status_generousailastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Generous_Round_LastRound'), "p-value"]
s2_mod1_CI_status_generousailastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='AI_Generous_Round_LastRound'), "95% CI"]

s2_mod1_beta_status_generoushumanmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Generous_Round_MiddleRound'), "B"]
s2_mod1_se_status_generoushumanmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Generous_Round_MiddleRound'), "SE"]
s2_mod1_t_status_generoushumanmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Generous_Round_MiddleRound'), "t-value"]
s2_mod1_p_status_generoushumanmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Generous_Round_MiddleRound'), "p-value"]
s2_mod1_CI_status_generoushumanmiddleround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Generous_Round_MiddleRound'), "95% CI"]

s2_mod1_beta_status_generoushumanlastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Generous_Round_LastRound'), "B"]
s2_mod1_se_status_generoushumanlastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Generous_Round_LastRound'), "SE"]
s2_mod1_t_status_generoushumanlastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Generous_Round_LastRound'), "t-value"]
s2_mod1_p_status_generoushumanlastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Generous_Round_LastRound'), "p-value"]
s2_mod1_CI_status_generoushumanlastround = s2_mod1_sigslopes1[which(s2_mod1_sigslopes1$Reference=='Human_Generous_Round_LastRound'), "95% CI"]

```

We found significant main effects of agency (B = `r s2_mod1_beta_agency`, SE = `r s2_mod1_se_agency`, t = `r s2_mod1_t_agency`, p = `r s2_mod1_p_agency`, CI = `r s2_mod1_CI_agency`), status (B = `r s2_mod1_beta_status`, SE = `r s2_mod1_se_status`, t = `r s2_mod1_t_status`, p = `r s2_mod1_p_status`, CI = `r s2_mod1_CI_status`), generosity (B = `r s2_mod1_beta_generosity`, SE = `r s2_mod1_se_generosity`, t = `r s2_mod1_t_generosity`, p = `r s2_mod1_p_generosity`, CI = `r s2_mod1_CI_generosity`), and round (B = `r s2_mod1_beta_round`, SE = `r s2_mod1_se_round`, t = `r s2_mod1_t_round`, p = `r s2_mod1_p_round`, CI = `r s2_mod1_CI_round`), which were further qualified by a significant interaction effect of agency, status, generosity, and rounds (B = `r s2_mod1_beta_agencystatusgenerosityround`, SE = `r s2_mod1_se_agencystatusgenerosityround`, t = `r s2_mod1_t_agencystatusgenerosityround`, p = `r s2_mod1_p_agencystatusgenerosityround`, CI = `r s2_mod1_CI_agencystatusgenerosityround`). 

Decomposing this interaction, we found that participants decreased in trust over rounds for partners of all agency, status, and generosity combinations(Low status Greedy AI: B = `r s2_mod1_beta_round_lowstatusgreedyai`, SE = `r s2_mod1_se_round_lowstatusgreedyai`, t = `r s2_mod1_t_round_lowstatusgreedyai`, p = `r s2_mod1_p_round_lowstatusgreedyai`, CI = `r s2_mod1_CI_round_lowstatusgreedyai`; Low status Neutral AI: B = `r s2_mod1_beta_round_lowstatusneutralai`, SE = `r s2_mod1_se_round_lowstatusneutralai`, t = `r s2_mod1_t_round_lowstatusneutralai`, p = `r s2_mod1_p_round_lowstatusneutralai`, CI = `r s2_mod1_CI_round_lowstatusneutralai`; Low status Generous AI: B = `r s2_mod1_beta_round_lowstatusgenerousai`, SE = `r s2_mod1_se_round_lowstatusgenerousai`, t = `r s2_mod1_t_round_lowstatusgenerousai`, p = `r s2_mod1_p_round_lowstatusgenerousai`, CI = `r s2_mod1_CI_round_lowstatusgenerousai`; High status Greedy AI: B = `r s2_mod1_beta_round_highstatusgreedyai`, SE = `r s2_mod1_se_round_highstatusgreedyai`, t = `r s2_mod1_t_round_highstatusgreedyai`, p = `r s2_mod1_p_round_highstatusgreedyai`, CI = `r s2_mod1_CI_round_highstatusgreedyai`; High status Neutral AI: B = `r s2_mod1_beta_round_highstatusneutralai`, SE = `r s2_mod1_se_round_highstatusneutralai`, t = `r s2_mod1_t_round_highstatusneutralai`, p = `r s2_mod1_p_round_highstatusneutralai`, CI = `r s2_mod1_CI_round_highstatusneutralai`; High status Generous AI: B = `r s2_mod1_beta_round_highstatusgenerousai`, SE = `r s2_mod1_se_round_highstatusgenerousai`, t = `r s2_mod1_t_round_highstatusgenerousai`, p = `r s2_mod1_p_round_highstatusgenerousai`, CI = `r s2_mod1_CI_round_highstatusgenerousai`; Low status Greedy Human: B = `r s2_mod1_beta_round_lowstatusgreedyhuman`, SE = `r s2_mod1_se_round_lowstatusgreedyhuman`, t = `r s2_mod1_t_round_lowstatusgreedyhuman`, p = `r s2_mod1_p_round_lowstatusgreedyhuman`, CI = `r s2_mod1_CI_round_lowstatusgreedyhuman`; Low status Neutral Human: B = `r s2_mod1_beta_round_lowstatusneutralhuman`, SE = `r s2_mod1_se_round_lowstatusneutralhuman`, t = `r s2_mod1_t_round_lowstatusneutralhuman`, p = `r s2_mod1_p_round_lowstatusneutralhuman`, CI = `r s2_mod1_CI_round_lowstatusneutralhuman`; Low status Generous Human: B = `r s2_mod1_beta_round_lowstatusgeneroushuman`, SE = `r s2_mod1_se_round_lowstatusgeneroushuman`, t = `r s2_mod1_t_round_lowstatusgeneroushuman`, p = `r s2_mod1_p_round_lowstatusgeneroushuman`, CI = `r s2_mod1_CI_round_lowstatusgeneroushuman`; High status Greedy Human: B = `r s2_mod1_beta_round_highstatusgreedyhuman`, SE = `r s2_mod1_se_round_highstatusgreedyhuman`, t = `r s2_mod1_t_round_highstatusgreedyhuman`, p = `r s2_mod1_p_round_highstatusgreedyhuman`, CI = `r s2_mod1_CI_round_highstatusgreedyhuman`; High status Neutral Human: B = `r s2_mod1_beta_round_highstatusneutralhuman`, SE = `r s2_mod1_se_round_highstatusneutralhuman`, t = `r s2_mod1_t_round_highstatusneutralhuman`, p = `r s2_mod1_p_round_highstatusneutralhuman`, CI = `r s2_mod1_CI_round_highstatusneutralhuman`; High status Generous Human: B = `r s2_mod1_beta_round_highstatusgeneroushuman`, SE = `r s2_mod1_se_round_highstatusgeneroushuman`, t = `r s2_mod1_t_round_highstatusgeneroushuman`, p = `r s2_mod1_p_round_highstatusgeneroushuman`, CI = `r s2_mod1_CI_round_highstatusgeneroushuman`). 

We also found that participants consistently trusted generous partners more than greedy partners for partners of all agency, status, and generosity combinations (Low status AI First Round: B = `r s2_mod1_beta_generosity_ailowstatusfirstround`, SE = `r s2_mod1_se_generosity_ailowstatusfirstround`, t = `r s2_mod1_t_generosity_ailowstatusfirstround`, p = `r s2_mod1_p_generosity_ailowstatusfirstround`, CI = `r s2_mod1_CI_generosity_ailowstatusfirstround`; Low status AI Middle Round: B = `r s2_mod1_beta_generosity_ailowstatusmiddleround`, SE = `r s2_mod1_se_generosity_ailowstatusmiddleround`, t = `r s2_mod1_t_generosity_ailowstatusmiddleround`, p = `r s2_mod1_p_generosity_ailowstatusmiddleround`, CI = `r s2_mod1_CI_generosity_ailowstatusmiddleround`; Low status AI Last Round: B = `r s2_mod1_beta_generosity_ailowstatuslastround`, SE = `r s2_mod1_se_generosity_ailowstatuslastround`, t = `r s2_mod1_t_generosity_ailowstatuslastround`, p = `r s2_mod1_p_generosity_ailowstatuslastround`, CI = `r s2_mod1_CI_generosity_ailowstatuslastround`; High status AI First Round: B = `r s2_mod1_beta_generosity_aihighstatusfirstround`, SE = `r s2_mod1_se_generosity_aihighstatusfirstround`, t = `r s2_mod1_t_generosity_aihighstatusfirstround`, p = `r s2_mod1_p_generosity_aihighstatusfirstround`, CI = `r s2_mod1_CI_generosity_aihighstatusfirstround`; High status AI Middle Round: B = `r s2_mod1_beta_generosity_aihighstatusmiddleround`, SE = `r s2_mod1_se_generosity_aihighstatusmiddleround`, t = `r s2_mod1_t_generosity_aihighstatusmiddleround`, p = `r s2_mod1_p_generosity_aihighstatusmiddleround`, CI = `r s2_mod1_CI_generosity_aihighstatusmiddleround`; High status AI Last Round: B = `r s2_mod1_beta_generosity_aihighstatuslastround`, SE = `r s2_mod1_se_generosity_aihighstatuslastround`, t = `r s2_mod1_t_generosity_aihighstatuslastround`, p = `r s2_mod1_p_generosity_aihighstatuslastround`, CI = `r s2_mod1_CI_generosity_aihighstatuslastround`; Low status Human First Round: B = `r s2_mod1_beta_generosity_humanlowstatusfirstround`, SE = `r s2_mod1_se_generosity_humanlowstatusfirstround`, t = `r s2_mod1_t_generosity_humanlowstatusfirstround`, p = `r s2_mod1_p_generosity_humanlowstatusfirstround`, CI = `r s2_mod1_CI_generosity_humanlowstatusfirstround`; Low status Human Middle Round: B = `r s2_mod1_beta_generosity_humanlowstatusmiddleround`, SE = `r s2_mod1_se_generosity_humanlowstatusmiddleround`, t = `r s2_mod1_t_generosity_humanlowstatusmiddleround`, p = `r s2_mod1_p_generosity_humanlowstatusmiddleround`, CI = `r s2_mod1_CI_generosity_humanlowstatusmiddleround`; Low status Human Last Round: B = `r s2_mod1_beta_generosity_humanlowstatuslastround`, SE = `r s2_mod1_se_generosity_humanlowstatuslastround`, t = `r s2_mod1_t_generosity_humanlowstatuslastround`, p = `r s2_mod1_p_generosity_humanlowstatuslastround`, CI = `r s2_mod1_CI_generosity_humanlowstatuslastround`; High status Human First Round: B = `r s2_mod1_beta_generosity_humanhighstatusfirstround`, SE = `r s2_mod1_se_generosity_humanhighstatusfirstround`, t = `r s2_mod1_t_generosity_humanhighstatusfirstround`, p = `r s2_mod1_p_generosity_humanhighstatusfirstround`, CI = `r s2_mod1_CI_generosity_humanhighstatusfirstround`; High status Human Middle Round: B = `r s2_mod1_beta_generosity_humanhighstatusmiddleround`, SE = `r s2_mod1_se_generosity_humanhighstatusmiddleround`, t = `r s2_mod1_t_generosity_humanhighstatusmiddleround`, p = `r s2_mod1_p_generosity_humanhighstatusmiddleround`, CI = `r s2_mod1_CI_generosity_humanhighstatusmiddleround`; High status Human Last Round: B = `r s2_mod1_beta_generosity_humanhighstatuslastround`, SE = `r s2_mod1_se_generosity_humanhighstatuslastround`, t = `r s2_mod1_t_generosity_humanhighstatuslastround`, p = `r s2_mod1_p_generosity_humanhighstatuslastround`, CI = `r s2_mod1_CI_generosity_humanhighstatuslastround`). 

Agency on the other hand only significantly affected trust decisions in first and middle rounds. Participants trusted human partners more than AI partners regardless of status and generosity from rounds 1 (Low status Greedy First Round: B = `r s2_mod1_beta_agency_lowstatusgreedyfirstround`, SE = `r s2_mod1_se_agency_lowstatusgreedyfirstround`, t = `r s2_mod1_t_agency_lowstatusgreedyfirstround`, p = `r s2_mod1_p_agency_lowstatusgreedyfirstround`, CI = `r s2_mod1_CI_agency_lowstatusgreedyfirstround`; Low status Neutral First Round: B = `r s2_mod1_beta_agency_lowstatusneutralfirstround`, SE = `r s2_mod1_se_agency_lowstatusneutralfirstround`, t = `r s2_mod1_t_agency_lowstatusneutralfirstround`, p = `r s2_mod1_p_agency_lowstatusneutralfirstround`, CI = `r s2_mod1_CI_agency_lowstatusneutralfirstround`; Low status Generous First Round: B = `r s2_mod1_beta_agency_lowstatusgenerousfirstround`, SE = `r s2_mod1_se_agency_lowstatusgenerousfirstround`, t = `r s2_mod1_t_agency_lowstatusgenerousfirstround`, p = `r s2_mod1_p_agency_lowstatusgenerousfirstround`, CI = `r s2_mod1_CI_agency_lowstatusgenerousfirstround`; High status Greedy First Round: B = `r s2_mod1_beta_agency_highstatusgreedyfirstround`, SE = `r s2_mod1_se_agency_highstatusgreedyfirstround`, t = `r s2_mod1_t_agency_highstatusgreedyfirstround`, p = `r s2_mod1_p_agency_highstatusgreedyfirstround`, CI = `r s2_mod1_CI_agency_highstatusgreedyfirstround`; High status Neutral First Round: B = `r s2_mod1_beta_agency_highstatusneutralfirstround`, SE = `r s2_mod1_se_agency_highstatusneutralfirstround`, t = `r s2_mod1_t_agency_highstatusneutralfirstround`, p = `r s2_mod1_p_agency_highstatusneutralfirstround`, CI = `r s2_mod1_CI_agency_highstatusneutralfirstround`; High status Generous First Round: B = `r s2_mod1_beta_agency_highstatusgenerousfirstround`, SE = `r s2_mod1_se_agency_highstatusgenerousfirstround`, t = `r s2_mod1_t_agency_highstatusgenerousfirstround`, p = `r s2_mod1_p_agency_highstatusgenerousfirstround`, CI = `r s2_mod1_CI_agency_highstatusgenerousfirstround`) to 5 (Low status Greedy Middle Round: B = `r s2_mod1_beta_agency_lowstatusgreedymiddleround`, SE = `r s2_mod1_se_agency_lowstatusgreedymiddleround`, t = `r s2_mod1_t_agency_lowstatusgreedymiddleround`, p = `r s2_mod1_p_agency_lowstatusgreedymiddleround`, CI = `r s2_mod1_CI_agency_lowstatusgreedymiddleround`; Low status Neutral Middle Round: B = `r s2_mod1_beta_agency_lowstatusneutralmiddleround`, SE = `r s2_mod1_se_agency_lowstatusneutralmiddleround`, t = `r s2_mod1_t_agency_lowstatusneutralmiddleround`, p = `r s2_mod1_p_agency_lowstatusneutralmiddleround`, CI = `r s2_mod1_CI_agency_lowstatusneutralmiddleround`; Low status Generous Middle Round: B = `r s2_mod1_beta_agency_lowstatusgenerousmiddleround`, SE = `r s2_mod1_se_agency_lowstatusgenerousmiddleround`, t = `r s2_mod1_t_agency_lowstatusgenerousmiddleround`, p = `r s2_mod1_p_agency_lowstatusgenerousmiddleround`, CI = `r s2_mod1_CI_agency_lowstatusgenerousmiddleround`; High status Greedy Middle Round: B = `r s2_mod1_beta_agency_highstatusgreedymiddleround`, SE = `r s2_mod1_se_agency_highstatusgreedymiddleround`, t = `r s2_mod1_t_agency_highstatusgreedymiddleround`, p = `r s2_mod1_p_agency_highstatusgreedymiddleround`, CI = `r s2_mod1_CI_agency_highstatusgreedymiddleround`; High status Neutral Middle Round: B = `r s2_mod1_beta_agency_highstatusneutralmiddleround`, SE = `r s2_mod1_se_agency_highstatusneutralmiddleround`, t = `r s2_mod1_t_agency_highstatusneutralmiddleround`, p = `r s2_mod1_p_agency_highstatusneutralmiddleround`, CI = `r s2_mod1_CI_agency_highstatusneutralmiddleround`; High status Generous Middle Round: B = `r s2_mod1_beta_agency_highstatusgenerousmiddleround`, SE = `r s2_mod1_se_agency_highstatusgenerousmiddleround`, t = `r s2_mod1_t_agency_highstatusgenerousmiddleround`, p = `r s2_mod1_p_agency_highstatusgenerousmiddleround`, CI = `r s2_mod1_CI_agency_highstatusgenerousmiddleround`). However by the last round this significant difference had disappeared.

Status effects were more complex. For human partners, status affected trust in middle and last rounds when the partners were greedy (middle round: B = `r s2_mod1_beta_status_greedyhumanmiddleround`, SE = `r s2_mod1_se_status_greedyhumanmiddleround`, t = `r s2_mod1_t_status_greedyhumanmiddleround`, p = `r s2_mod1_p_status_greedyhumanmiddleround`, CI = `r s2_mod1_CI_status_greedyhumanmiddleround`; last round: B = `r s2_mod1_beta_status_greedyhumanlastround`, SE = `r s2_mod1_se_status_greedyhumanlastround`, t = `r s2_mod1_t_status_greedyhumanlastround`, p = `r s2_mod1_p_status_greedyhumanlastround`, CI = `r s2_mod1_CI_status_greedyhumanlastround`) or generous (middle round: B = `r s2_mod1_beta_status_generoushumanmiddleround`, SE = `r s2_mod1_se_status_generoushumanmiddleround`, t = `r s2_mod1_t_status_generoushumanmiddleround`, p = `r s2_mod1_p_status_generoushumanmiddleround`, CI = `r s2_mod1_CI_status_generoushumanmiddleround`; last round: B = `r s2_mod1_beta_status_generoushumanlastround`, SE = `r s2_mod1_se_status_generoushumanlastround`, t = `r s2_mod1_t_status_generoushumanlastround`, p = `r s2_mod1_p_status_generoushumanlastround`, CI = `r s2_mod1_CI_status_generoushumanlastround`). However, the coefficients show a negative relationship - participants trusted low status human partners more when they were generous or greedy, from rounds 5 to 10, than high status partners. For neutral human partners, high status partners were trusted more than low status partners at round 1 (B = `r s2_mod1_beta_status_neutralhumanfirstround`, SE = `r s2_mod1_se_status_neutralhumanfirstround`, t = `r s2_mod1_t_status_neutralhumanfirstround`, p = `r s2_mod1_p_status_neutralhumanfirstround`, CI = `r s2_mod1_CI_status_neutralhumanfirstround`), but this significant effect had disappeared by round 5. For AI partners, status affected trust in the last round for greedy partners (B = `r s2_mod1_beta_status_greedyailastround`, SE = `r s2_mod1_se_status_greedyailastround`, t = `r s2_mod1_t_status_greedyailastround`, p = `r s2_mod1_p_status_greedyailastround`, CI = `r s2_mod1_CI_status_greedyailastround`) and in the middle and last rounds for generous partners (middle round: B = `r s2_mod1_beta_status_generousaimiddleround`, SE = `r s2_mod1_se_status_generousaimiddleround`, t = `r s2_mod1_t_status_generousaimiddleround`, p = `r s2_mod1_p_status_generousaimiddleround`, CI = `r s2_mod1_CI_status_generousaimiddleround`; last round: B = `r s2_mod1_beta_status_generousailastround`, SE = `r s2_mod1_se_status_generousailastround`, t = `r s2_mod1_t_status_generousailastround`, p = `r s2_mod1_p_status_generousailastround`, CI = `r s2_mod1_CI_status_generousailastround`). Once again, the coefficients showed a negative relationship - participants trusted low status partners more than high status partners. For neutral AI partners, high status partners were trusted more than low status partners from the first to the middle round (first round: B = `r s2_mod1_beta_status_neutralaifirstround`, SE = `r s2_mod1_se_status_neutralaifirstround`, t = `r s2_mod1_t_status_neutralaifirstround`, p = `r s2_mod1_p_status_neutralaifirstround`, CI = `r s2_mod1_CI_status_neutralaifirstround`; middle round: B = `r s2_mod1_beta_status_neutralaimiddleround`, SE = `r s2_mod1_se_status_neutralaimiddleround`, t = `r s2_mod1_t_status_neutralaimiddleround`, p = `r s2_mod1_p_status_neutralaimiddleround`, CI = `r s2_mod1_CI_status_neutralaimiddleround`).

## Model 2

```{r, include=FALSE, echo=FALSE, warning=FALSE}
s2_mod2_beta_generosity = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Reciprocity rate"), "B"]
s2_mod2_se_generosity = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Reciprocity rate"), "SE"]
s2_mod2_t_generosity = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Reciprocity rate"), "t-value"]
s2_mod2_p_generosity = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Reciprocity rate"), "p-value"]
s2_mod2_CI_generosity = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Reciprocity rate"), "95% CI"]

s2_mod2_beta_status = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Status"), "B"]
s2_mod2_se_status = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Status"), "SE"]
s2_mod2_t_status = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Status"), "t-value"]
s2_mod2_p_status = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Status"), "p-value"]
s2_mod2_CI_status = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Status"), "95% CI"]

s2_mod2_beta_feedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Feedback"), "B"]
s2_mod2_se_feedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Feedback"), "SE"]
s2_mod2_t_feedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Feedback"), "t-value"]
s2_mod2_p_feedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Feedback"), "p-value"]
s2_mod2_CI_feedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Feedback"), "95% CI"]

s2_mod2_beta_agencygenerositystatus = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Agency x Reciprocity rate x Status"), "B"]
s2_mod2_se_agencygenerositystatus = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Agency x Reciprocity rate x Status"), "SE"]
s2_mod2_t_agencygenerositystatus = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Agency x Reciprocity rate x Status"), "t-value"]
s2_mod2_p_agencygenerositystatus = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Agency x Reciprocity rate x Status"), "p-value"]
s2_mod2_CI_agencygenerositystatus = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Agency x Reciprocity rate x Status"), "95% CI"]

s2_mod2_beta_agencyfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Agency x Feedback"), "B"]
s2_mod2_se_agencyfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Agency x Feedback"), "SE"]
s2_mod2_t_agencyfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Agency x Feedback"), "t-value"]
s2_mod2_p_agencyfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Agency x Feedback"), "p-value"]
s2_mod2_CI_agencyfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Agency x Feedback"), "95% CI"]

s2_mod2_beta_generosityfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Reciprocity rate x Feedback"), "B"]
s2_mod2_se_generosityfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Reciprocity rate x Feedback"), "SE"]
s2_mod2_t_generosityfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Reciprocity rate x Feedback"), "t-value"]
s2_mod2_p_generosityfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Reciprocity rate x Feedback"), "p-value"]
s2_mod2_CI_generosityfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Reciprocity rate x Feedback"), "95% CI"]

s2_mod2_beta_statusfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Status x Feedback"), "B"]
s2_mod2_se_statusfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Status x Feedback"), "SE"]
s2_mod2_t_statusfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Status x Feedback"), "t-value"]
s2_mod2_p_statusfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Status x Feedback"), "p-value"]
s2_mod2_CI_statusfeedback = s2_mod2_statstable[which(s2_mod2_statstable$Predictor=="Status x Feedback"), "95% CI"]
```
```{r, include=FALSE, echo=FALSE}
# Simple slopes for agency, status, and generosity interaction

s2_mod2_beta_generosity_highstatusai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_HighStatus'), "B"]
s2_mod2_se_generosity_highstatusai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_HighStatus'), "SE"]
s2_mod2_t_generosity_highstatusai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_HighStatus'), "t-value"]
s2_mod2_p_generosity_highstatusai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_HighStatus'), "p-value"]
s2_mod2_CI_generosity_highstatusai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_HighStatus'), "95% CI"]

s2_mod2_beta_generosity_lowstatusai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_LowStatus'), "B"]
s2_mod2_se_generosity_lowstatusai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_LowStatus'), "SE"]
s2_mod2_t_generosity_lowstatusai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_LowStatus'), "t-value"]
s2_mod2_p_generosity_lowstatusai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_LowStatus'), "p-value"]
s2_mod2_CI_generosity_lowstatusai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_LowStatus'), "95% CI"]

s2_mod2_beta_generosity_highstatushuman = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='Human_HighStatus'), "B"]
s2_mod2_se_generosity_highstatushuman = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='Human_HighStatus'), "SE"]
s2_mod2_t_generosity_highstatushuman = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='Human_HighStatus'), "t-value"]
s2_mod2_p_generosity_highstatushuman = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='Human_HighStatus'), "p-value"]
s2_mod2_CI_generosity_highstatushuman = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='Human_HighStatus'), "95% CI"]

s2_mod2_beta_generosity_lowstatushuman = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='Human_LowStatus'), "B"]
s2_mod2_se_generosity_lowstatushuman = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='Human_LowStatus'), "SE"]
s2_mod2_t_generosity_lowstatushuman = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='Human_LowStatus'), "t-value"]
s2_mod2_p_generosity_lowstatushuman = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='Human_LowStatus'), "p-value"]
s2_mod2_CI_generosity_lowstatushuman = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='Human_LowStatus'), "95% CI"]

s2_mod2_beta_status_neutralai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_Neutral'), "B"]
s2_mod2_se_status_neutralai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_Neutral'), "SE"]
s2_mod2_t_status_neutralai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_Neutral'), "t-value"]
s2_mod2_p_status_neutralai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_Neutral'), "p-value"]
s2_mod2_CI_status_neutralai = s2_mod2_sigslopes1[which(s2_mod2_sigslopes1$Reference=='AI_Neutral'), "95% CI"]
```
```{r, include=FALSE, echo=FALSE}
# Simple slopes for agency and feedback interaction

s2_mod2_beta_feedback_ai = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='AI'), "B"]
s2_mod2_se_feedback_ai = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='AI'), "SE"]
s2_mod2_t_feedback_ai = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='AI'), "t-value"]
s2_mod2_p_feedback_ai = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='AI'), "p-value"]
s2_mod2_CI_feedback_ai = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='AI'), "95% CI"]

s2_mod2_beta_feedback_human = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='Human'), "B"]
s2_mod2_se_feedback_human = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='Human'), "SE"]
s2_mod2_t_feedback_human = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='Human'), "t-value"]
s2_mod2_p_feedback_human = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='Human'), "p-value"]
s2_mod2_CI_feedback_human = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='Human'), "95% CI"]

s2_mod2_beta_agency_midfeedback = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='MidFeedback'), "B"]
s2_mod2_se_agency_midfeedback = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='MidFeedback'), "SE"]
s2_mod2_t_agency_midfeedback = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='MidFeedback'), "t-value"]
s2_mod2_p_agency_midfeedback = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='MidFeedback'), "p-value"]
s2_mod2_CI_agency_midfeedback = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='MidFeedback'), "95% CI"]

s2_mod2_beta_agency_highfeedback = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='HighFeedback'), "B"]
s2_mod2_se_agency_highfeedback = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='HighFeedback'), "SE"]
s2_mod2_t_agency_highfeedback = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='HighFeedback'), "t-value"]
s2_mod2_p_agency_highfeedback = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='HighFeedback'), "p-value"]
s2_mod2_CI_agency_highfeedback = s2_mod2_sigslopes2[which(s2_mod2_sigslopes2$Reference=='HighFeedback'), "95% CI"]
```
```{r, include=FALSE, echo=FALSE}
# Simple slopes for status and feedback interaction

s2_mod2_beta_status_lowfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='LowFeedback'), "B"]
s2_mod2_se_status_lowfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='LowFeedback'), "SE"]
s2_mod2_t_status_lowfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='LowFeedback'), "t-value"]
s2_mod2_p_status_lowfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='LowFeedback'), "p-value"]
s2_mod2_CI_status_lowfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='LowFeedback'), "95% CI"]

s2_mod2_beta_status_midfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='MidFeedback'), "B"]
s2_mod2_se_status_midfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='MidFeedback'), "SE"]
s2_mod2_t_status_midfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='MidFeedback'), "t-value"]
s2_mod2_p_status_midfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='MidFeedback'), "p-value"]
s2_mod2_CI_status_midfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='MidFeedback'), "95% CI"]

s2_mod2_beta_status_highfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='HighFeedback'), "B"]
s2_mod2_se_status_highfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='HighFeedback'), "SE"]
s2_mod2_t_status_highfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='HighFeedback'), "t-value"]
s2_mod2_p_status_highfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='HighFeedback'), "p-value"]
s2_mod2_CI_status_highfeedback = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='HighFeedback'), "95% CI"]

s2_mod2_beta_feedback_lowstatus = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='LowStatus'), "B"]
s2_mod2_se_feedback_lowstatus = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='LowStatus'), "SE"]
s2_mod2_t_feedback_lowstatus = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='LowStatus'), "t-value"]
s2_mod2_p_feedback_lowstatus = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='LowStatus'), "p-value"]
s2_mod2_CI_feedback_lowstatus = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='LowStatus'), "95% CI"]

s2_mod2_beta_feedback_highstatus = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='HighStatus'), "B"]
s2_mod2_se_feedback_highstatus = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='HighStatus'), "SE"]
s2_mod2_t_feedback_highstatus = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='HighStatus'), "t-value"]
s2_mod2_p_feedback_highstatus = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='HighStatus'), "p-value"]
s2_mod2_CI_feedback_highstatus = s2_mod2_sigslopes3[which(s2_mod2_sigslopes3$Reference=='HighStatus'), "95% CI"]
```
```{r, include=FALSE, echo=FALSE}
# Simple slopes for generosity and feedback interaction

s2_mod2_beta_feedback_greedy = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Greedy'), "B"]
s2_mod2_se_feedback_greedy = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Greedy'), "SE"]
s2_mod2_t_feedback_greedy = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Greedy'), "t-value"]
s2_mod2_p_feedback_greedy = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Greedy'), "p-value"]
s2_mod2_CI_feedback_greedy = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Greedy'), "95% CI"]

s2_mod2_beta_feedback_neutral = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Neutral'), "B"]
s2_mod2_se_feedback_neutral = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Neutral'), "SE"]
s2_mod2_t_feedback_neutral = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Neutral'), "t-value"]
s2_mod2_p_feedback_neutral = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Neutral'), "p-value"]
s2_mod2_CI_feedback_neutral = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Neutral'), "95% CI"]

s2_mod2_beta_feedback_generous = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Generous'), "B"]
s2_mod2_se_feedback_generous = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Generous'), "SE"]
s2_mod2_t_feedback_generous = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Generous'), "t-value"]
s2_mod2_p_feedback_generous = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Generous'), "p-value"]
s2_mod2_CI_feedback_generous = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='Generous'), "95% CI"]

s2_mod2_beta_generosity_lowfeedback = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='LowFeedback'), "B"]
s2_mod2_se_generosity_lowfeedback = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='LowFeedback'), "SE"]
s2_mod2_t_generosity_lowfeedback = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='LowFeedback'), "t-value"]
s2_mod2_p_generosity_lowfeedback = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='LowFeedback'), "p-value"]
s2_mod2_CI_generosity_lowfeedback = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='LowFeedback'), "95% CI"]

s2_mod2_beta_generosity_midfeedback = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='MidFeedback'), "B"]
s2_mod2_se_generosity_midfeedback = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='MidFeedback'), "SE"]
s2_mod2_t_generosity_midfeedback = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='MidFeedback'), "t-value"]
s2_mod2_p_generosity_midfeedback = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='MidFeedback'), "p-value"]
s2_mod2_CI_generosity_midfeedback = s2_mod2_sigslopes4[which(s2_mod2_sigslopes4$Reference=='MidFeedback'), "95% CI"]
```

We found significant main effects of generosity (B = `r s2_mod2_beta_generosity`, SE = `r s2_mod2_se_generosity`, t = `r s2_mod2_t_generosity`, p = `r s2_mod2_p_generosity`, CI = `r s2_mod2_CI_generosity`), status (B = `r s2_mod2_beta_status`, SE = `r s2_mod2_se_status`, t = `r s2_mod2_t_status`, p = `r s2_mod2_p_status`, CI = `r s2_mod2_CI_status`), and feedback (B = `r s2_mod2_beta_feedback`, SE = `r s2_mod2_se_feedback`, t = `r s2_mod2_t_feedback`, p = `r s2_mod2_p_feedback`, CI = `r s2_mod2_CI_feedback`), which were further qualified by two-way interactions between generosity & feedback (B = `r s2_mod2_beta_generosityfeedback`, SE = `r s2_mod2_se_generosityfeedback`, t = `r s2_mod2_t_generosityfeedback`, p = `r s2_mod2_p_generosityfeedback`, CI = `r s2_mod2_CI_generosityfeedback`), and status & feedback (B = `r s2_mod2_beta_statusfeedback`, SE = `r s2_mod2_se_statusfeedback`, t = `r s2_mod2_t_statusfeedback`, p = `r s2_mod2_p_statusfeedback`, CI = `r s2_mod2_CI_statusfeedback`). While we saw no main effects of agency, we found a two-way interaction between agency & feedback (B = `r s2_mod2_beta_agencyfeedback`, SE = `r s2_mod2_se_agencyfeedback`, t = `r s2_mod2_t_agencyfeedback`, p = `r s2_mod2_p_agencyfeedback`, CI = `r s2_mod2_CI_agencyfeedback`), and a three-way interaction between agency, status, & generosity (B = `r s2_mod2_beta_agencygenerositystatus`, SE = `r s2_mod2_se_agencygenerositystatus`, t = `r s2_mod2_t_agencygenerositystatus`, p = `r s2_mod2_p_agencygenerositystatus`, CI = `r s2_mod2_CI_agencygenerositystatus`).

Our simple slopes analyses revealed that increase in feedback led to an increase in trust towards greedy (B = `r s2_mod2_beta_feedback_greedy`, SE = `r s2_mod2_se_feedback_greedy`, t = `r s2_mod2_t_feedback_greedy`, p = `r s2_mod2_p_feedback_greedy`, CI = `r s2_mod2_CI_feedback_greedy`), neutral (B = `r s2_mod2_beta_feedback_neutral`, SE = `r s2_mod2_se_feedback_neutral`, t = `r s2_mod2_t_feedback_neutral`, p = `r s2_mod2_p_feedback_neutral`, CI = `r s2_mod2_CI_feedback_neutral`), & generous partners (B = `r s2_mod2_beta_feedback_generous`, SE = `r s2_mod2_se_feedback_generous`, t = `r s2_mod2_t_feedback_generous`, p = `r s2_mod2_p_feedback_generous`, CI = `r s2_mod2_CI_feedback_generous`). They trusted generous partners more than neutral or generous partners at low (B = `r s2_mod2_beta_generosity_lowfeedback`, SE = `r s2_mod2_se_generosity_lowfeedback`, t = `r s2_mod2_t_generosity_lowfeedback`, p = `r s2_mod2_p_generosity_lowfeedback`, CI = `r s2_mod2_CI_generosity_lowfeedback`) and medium levels of feedback (B = `r s2_mod2_beta_generosity_midfeedback`, SE = `r s2_mod2_se_generosity_midfeedback`, t = `r s2_mod2_t_generosity_midfeedback`, p = `r s2_mod2_p_generosity_midfeedback`, CI = `r s2_mod2_CI_generosity_midfeedback`), but by high levels of feedback there was no significant differences in trust towards generous, neutral, and greedy partners.

Increase in feedback also increased trust towards low (B = `r s2_mod2_beta_feedback_lowstatus`, SE = `r s2_mod2_se_feedback_lowstatus`, t = `r s2_mod2_t_feedback_lowstatus`, p = `r s2_mod2_p_feedback_lowstatus`, CI = `r s2_mod2_CI_feedback_lowstatus`) & high status partners (B = `r s2_mod2_beta_feedback_highstatus`, SE = `r s2_mod2_se_feedback_highstatus`, t = `r s2_mod2_t_feedback_highstatus`, p = `r s2_mod2_p_feedback_highstatus`, CI = `r s2_mod2_CI_feedback_highstatus`). Participants trusted high status partners more than low status partners low (B = `r s2_mod2_beta_status_lowfeedback`, SE = `r s2_mod2_se_status_lowfeedback`, t = `r s2_mod2_t_status_lowfeedback`, p = `r s2_mod2_p_status_lowfeedback`, CI = `r s2_mod2_CI_status_lowfeedback`), medium (B = `r s2_mod2_beta_status_midfeedback`, SE = `r s2_mod2_se_status_midfeedback`, t = `r s2_mod2_t_status_midfeedback`, p = `r s2_mod2_p_status_midfeedback`, CI = `r s2_mod2_CI_status_midfeedback`), and high feedback (B = `r s2_mod2_beta_status_highfeedback`, SE = `r s2_mod2_se_status_highfeedback`, t = `r s2_mod2_t_status_highfeedback`, p = `r s2_mod2_p_status_highfeedback`, CI = `r s2_mod2_CI_status_highfeedback`). 

Similarly, increase in feedback led to increase in trust towards both human (B = `r s2_mod2_beta_feedback_human`, SE = `r s2_mod2_se_feedback_human`, t = `r s2_mod2_t_feedback_human`, p = `r s2_mod2_p_feedback_human`, CI = `r s2_mod2_CI_feedback_human`) and AI partners (B = `r s2_mod2_beta_feedback_ai`, SE = `r s2_mod2_se_feedback_ai`, t = `r s2_mod2_t_feedback_ai`, p = `r s2_mod2_p_feedback_ai`, CI = `r s2_mod2_CI_feedback_ai`). Participants trusted human partners more than AI partners at medium (B = `r s2_mod2_beta_agency_midfeedback`, SE = `r s2_mod2_se_agency_midfeedback`, t = `r s2_mod2_t_agency_midfeedback`, p = `r s2_mod2_p_agency_midfeedback`, CI = `r s2_mod2_CI_agency_midfeedback`) and high levels of feedback (B = `r s2_mod2_beta_agency_highfeedback`, SE = `r s2_mod2_se_agency_highfeedback`, t = `r s2_mod2_t_agency_highfeedback`, p = `r s2_mod2_p_agency_highfeedback`, CI = `r s2_mod2_CI_agency_highfeedback`), but not at low levels of feedback. 

Decomposing the three-way interaction, we found that participants trusted generous more than neutral or greedy partners for low status humans (B = `r s2_mod2_beta_generosity_lowstatushuman`, SE = `r s2_mod2_se_generosity_lowstatushuman`, t = `r s2_mod2_t_generosity_lowstatushuman`, p = `r s2_mod2_p_generosity_lowstatushuman`, CI = `r s2_mod2_CI_generosity_lowstatushuman`), low status AI (B = `r s2_mod2_beta_generosity_lowstatusai`, SE = `r s2_mod2_se_generosity_lowstatusai`, t = `r s2_mod2_t_generosity_lowstatusai`, p = `r s2_mod2_p_generosity_lowstatusai`, CI = `r s2_mod2_CI_generosity_lowstatusai`), high status humans (B = `r s2_mod2_beta_generosity_highstatushuman`, SE = `r s2_mod2_se_generosity_highstatushuman`, t = `r s2_mod2_t_generosity_highstatushuman`, p = `r s2_mod2_p_generosity_highstatushuman`, CI = `r s2_mod2_CI_generosity_highstatushuman`), and high status AI (B = `r s2_mod2_beta_generosity_highstatusai`, SE = `r s2_mod2_se_generosity_highstatusai`, t = `r s2_mod2_t_generosity_highstatusai`, p = `r s2_mod2_p_generosity_highstatusai`, CI = `r s2_mod2_CI_generosity_highstatusai`). Participants also trusted high status partners more than low status partners for neutral AI partners (B = `r s2_mod2_beta_status_neutralai`, SE = `r s2_mod2_se_status_neutralai`, t = `r s2_mod2_t_status_neutralai`, p = `r s2_mod2_p_status_neutralai`, CI = `r s2_mod2_CI_status_neutralai`).

Overall, we replicated the generosity & feedback and status & feedback found in study 1. The agency and generosity we had discovered in study 1 was qualified by a three-way interaction that included status. We also found an additional interaction - effects of agency in interaction with feedback, and with status & generosity.

Altogether, our results show that decision-making in an economic context where partners differ on agency, status, and generosity is complex. While we did not test participants for what they thought competency status meant, our results suggest that it participants did not trust high status partners in all contexts.
